---
title: "analisi preliminare"
author: "MNB"
date: "4/25/2024"
output: html_document
---

# load libraries
```{r}
library(plyr)
library(dplyr)
library(tidyverse)
library(tidyr)
library(naniar)
library(ggplot2)
library(stargazer)
library(brms)
library(sandwich)
library(lmtest)
library(magrittr) # for pipes
library(nnet) # for the multinom()-function
library(MASS) # for the multivariate normal distribution

# The package
library(MNLpred)

# Plotting the predicted probabilities:
library(scales)

```


# Remove lists 
```{r, include=FALSE}
## remove lists
rm(list=ls())
```

# Functions
```{r}
# exclude
'%!in%' <- function(x,y)!('%in%'(x,y))

# Function to scale a variable to the 0-1 range
scale_0_1 <- function(x) {
  (x - min(x, na.rm = TRUE)) / (max(x, na.rm = TRUE) - min(x, na.rm = TRUE))
}


# Define the function to generate a variable chain suitable for a model
gen_formula <- function(dependent_var, var_list) {
  # Concatenate the variable names with " + " as separator
  var_chain <- paste(var_list, collapse = " + ")

  complete_formula <- as.formula(paste(dependent_var, var_chain, sep = " ~ "))

    
  # Return the concatenated variable chain
  return(complete_formula)
}


```


# Import DFs
## Set folders
```{r}
## set url
desktop_path <- file.path("C:", "Users", "marco", "Desktop")
main_folder_name <- "DFGlobalLab"
sub_folder_name <- "Compiled"
```

## Import Globsol dataset
### 5k
```{r}
# set DF
DF<-c("globsol_20240313_df5k.rds")
# load DF
Df_path <- file.path(desktop_path, main_folder_name, sub_folder_name, DF )
# importing DF 
df_Globsol5k <- readRDS(Df_path)

```

### 50k
```{r}
# set DF
DF<-c("globsol_20240313_df50k.rds")
# load DF
Df_path <- file.path(desktop_path, main_folder_name, sub_folder_name, DF )
# importing DF 
df_Globsol50k <- readRDS(Df_path)

```


### 100k
```{r}
# set DF
DF<-c("globsol_20240313_df100k.rds")
# load DF
Df_path <- file.path(desktop_path, main_folder_name, sub_folder_name, DF )
# importing DF 
df_Globsol100k <- readRDS(Df_path)

```


## Import Independent and control variables
```{r}
# set DF
DF<-c("df_ind_var.rds")
# load DF
Df_path <- file.path(desktop_path, main_folder_name, sub_folder_name, DF )
# importing DF 
df_IndVars <- readRDS(Df_path)

```

# Set dataset for analysis
```{r}
data<-df_Globsol50k
```



# Merge dfs
```{r}
df_full <- left_join(data, df_IndVars, by = c("year" = "year", "iso3c" = "iso3c"))

## remove useless vars
# keep var of interest
df_full <- df_full[ , names(df_full) %!in% c("country.x",
                                            "country.y",
                                            "country_wb",
                                            "disaster")] 
```

# start analysis
## preprocess data
```{r}

## select vars if interest
List<-c("count_HO_lag_1",
        "nat_rents_lag_1",
        "trade_part_lag_1",
        "exp_part_lag_1",
        "impo_part_lag_1",
        "N_donors_lag_1",
        "pop_tot_lag_1",
        "gdp_lag_1",
        "inflation_lag_1",
        "urb_pop_pct_lag_1",
        "trade_lag_1",
        "inf_mort_rate_lag_1",
        "liberal_demo_lag_1",
        "regime_corruption_lag_1",
        "civil_soc_lag_1",
        "best_fat_lag_1",
        "food_export_lag_1",
        "food_import_lag_1",
        "biological_dummy_50k",
        "biological_dummy_lag_1_50k",
        "climatological_dummy_50k",
        "climatological_dummy_lag_1_50k",
        "geophysical_dummy_50k",
        "geophysical_dummy_lag_1_50k",
        "hydrological_dummy_50k",
        "hydrological_dummy_lag_1_50k",
        "meteorological_dummy_50k",
        "meteorological_dummy_lag_1_50k",
        "colony_fra",
        "colony_gbr",
        "colony_oeu",
        "colony_prt",
        "colony_esp",
        "tropical",
        "desert",
        "N_memberships")


df_model_data <- df_full[ , names(df_full) %in% c(List,"GlobSol","iso3c","year")] 

## drop NAs
#df_model_data <- na.omit(df_model_data)

# List of variable names to scale
variables_to_scale <- List


# Apply  scaling function to the specified variables
df_scaled<-df_model_data


df_scaled$ln_GDP<-log(df_scaled$gdp_lag_1)
df_scaled$ln_pop_tot_lag_1<-log(df_scaled$pop_tot_lag_1)
df_scaled$ln_trade_lag_1<-log(df_scaled$trade_lag_1)

## set fixed effects
df_scaled$iso3c <- as.factor(df_scaled$iso3c)
df_scaled$year <- as.factor(df_scaled$year)

# Check the distribution of the Globsol variable
table(df_scaled$GlobSol)

#add index column to data frame
df_scaled$index <- 1:nrow(df_scaled)

##
df_scaled$colony<-ifelse(df_scaled$colony_fra==1|
                           df_scaled$colony_gbr==1|
                           df_scaled$colony_oeu==1 |
                           df_scaled$colony_prt==1 |
                           df_scaled$colony_esp==1,1,0)


# List of variable names to scale
#variables_to_scale <- c(List,"ln_GDP","ln_pop_tot_lag_1","ln_trade_lag_1")
#df_scaled[variables_to_scale] <- lapply(df_scaled[variables_to_scale], scale_0_1)

```

## Export file
```{r}
#saving it
namefile<-"df_full.csv"
folder_path_wb <- file.path(desktop_path, main_folder_name, sub_folder_name, namefile)
write.csv(df_scaled, folder_path_wb, row.names = FALSE)  # row.names = FALSE to exclude row indices

```

## Set variables
```{r}
# Define the dependent variable and set is as an unordered factors
dependent_var <- "GlobSol"
df_scaled$GlobSol <- factor(df_scaled$GlobSol)  # Ensure it's a factor
# Re-level the target variable to set 4 as the baseline
df_scaled$GlobSol <- relevel(df_scaled$GlobSol, ref = "4")


main_indip <- c("N_memberships", "ln_trade_lag_1", "nat_rents_lag_1")
main_indip_expo <- c("count_HO_lag_1", "exp_part_lag_1", "nat_rents_lag_1")
main_indip_impo <- c("count_HO_lag_1", "impo_part_lag_1", "nat_rents_lag_1")


econo <- c("ln_pop_tot_lag_1", "ln_GDP")
socio_poli <- c("liberal_demo_lag_1","regime_corruption_lag_1")
#conflict<- c("OneSided_fat_lag_1", "NonState_conf_fat_lag_1","StateBased_conf_fat_lag_1")
#development<- c("agricolture_va_lag_1", "inf_mort_rate_lag_1","urb_pop_pct_lag_1")
cof_deve<- c( "best_fat_lag_1", "urb_pop_pct_lag_1")
disaster<-c("biological_dummy_50k",
            "biological_dummy_lag_1_50k",
            "climatological_dummy_50k",
            "climatological_dummy_lag_1_50k",
            "geophysical_dummy_50k",
            "geophysical_dummy_lag_1_50k",
            "hydrological_dummy_50k",
            "hydrological_dummy_lag_1_50k",
            "meteorological_dummy_50k",
            "meteorological_dummy_lag_1_50k"
            )

geo_colonial<-c("colony",
        "tropical",
        "desert")

#```



## Run multinomial models
#```{r}
# baseline model
Vars<-main_indip
# Create the complete formula
complete_formula <-gen_formula(dependent_var,Vars)
# Estimate the multinomial logistic regression model
multinom_model1 <- multinom(complete_formula, data = df_scaled)

# Economic controls
Vars<-c(main_indip,econo)
# Create the complete formula
complete_formula <-gen_formula(dependent_var,Vars) 
# Estimate the multinomial logistic regression model
multinom_model2 <- multinom(complete_formula, data = df_scaled)


# Political controls
Vars<-c(main_indip,socio_poli)
# Create the complete formula
complete_formula <-gen_formula(dependent_var,Vars) 
# Estimate the multinomial logistic regression model
multinom_model3 <- multinom(complete_formula, data = df_scaled)

# dev controls
Vars<-c(main_indip,cof_deve)
# Create the complete formula
complete_formula <-gen_formula(dependent_var,Vars) 
# Estimate the multinomial logistic regression model
multinom_model4 <- multinom(complete_formula, data = df_scaled)

# disaster controls
Vars<-c(main_indip,disaster)
# Create the complete formula
complete_formula <-gen_formula(dependent_var,Vars) 
# Estimate the multinomial logistic regression model
multinom_model5 <- multinom(complete_formula, data = df_scaled)


# disaster controls
Vars<-c(main_indip,geo_colonial)
# Create the complete formula
complete_formula <-gen_formula(dependent_var,Vars) 
# Estimate the multinomial logistic regression model
multinom_model6 <- multinom(complete_formula, data = df_scaled)


# Full controls
Vars<-c(main_indip,econo,socio_poli,cof_deve, disaster, geo_colonial)
# Create the complete formula
complete_formula <-gen_formula(dependent_var,Vars) 
# Estimate the multinomial logistic regression model
multinom_model7 <- multinom(complete_formula, data = df_scaled)

# # Full controls
# Vars<-c(main_indip_impo,econo,socio_poli,cof_deve, disaster, geo_colonial)
# # Create the complete formula
# complete_formula <-gen_formula(dependent_var,Vars) 
# # Estimate the multinomial logistic regression model
# multinom_model8 <- multinom(complete_formula, data = df_scaled)
# 
# # Full controls
# Vars<-c(main_indip_expo,econo,socio_poli,cof_deve, disaster, geo_colonial)
# # Create the complete formula
# complete_formula <-gen_formula(dependent_var,Vars) 
# # Estimate the multinomial logistic regression model
# multinom_model9 <- multinom(complete_formula, data = df_scaled)


#```

## plot results tables
#```{r}
# Create a comparison table with stargazer
stargazer(
  multinom_model1, multinom_model2, multinom_model3, multinom_model4, multinom_model5, multinom_model6, multinom_model7, #multinom_model8, multinom_model9,
  type = "text",  # or "latex" or "html" for different output formats
  title = "Comparison of Multinomial Models",
  align = TRUE,
  no.space = TRUE,
  digits = 3,  # Number of decimal places to display
  column.labels = c("Model 1", "Model 2", "Model 3"),  # Label each model
  omit.stat = c("aic", "bic")  # Optionally omit some statistics for cleaner output
)
```

```{r}
summary(multinom_model7)

```


### probabilities with marginal intervals
```{r}


# Full controls
Vars<-c(main_indip,econo,socio_poli,cof_deve, disaster, geo_colonial)
# Create the complete formula
complete_formula <-gen_formula(dependent_var,Vars) 
# Estimate the multinomial logistic regression model
multinom_model7 <- multinom(complete_formula, data = df_scaled,
                            Hess = TRUE)

mod1<-multinom_model7
gles<-df_scaled

pred1 <- mnl_pred_ova(model = mod1,
                      data = gles,
                      x = "N_memberships",
                      by = 1,
                      seed = "random", # default
                      nsim = 100, # faster
                      probs = c(0.025, 0.975)) # default


pred1$plotdata %>% head()



ggplot(data = pred1$plotdata, aes(x = N_memberships, 
                                  y = mean,
                                  ymin = lower, ymax = upper)) +
  geom_ribbon(alpha = 0.1) + # Confidence intervals
  geom_line() + # Mean
  facet_wrap(.~ GlobSol, scales = "fixed", ncol = 2) +
  scale_y_continuous(labels = percent_format(accuracy = 1)) + # % labels
  scale_x_continuous(breaks = c(0,0.1,0.2,0.3,0.4,.5,0.6,0.8,0.9,1)) +
  theme_bw() +
  labs(y = "Predicted probabilities",
       x = "Head") # Always label your axes ;)



pred1 <- mnl_pred_ova(model = mod1,
                      data = gles,
                      x = "ln_trade_lag_1",
                      by = 0.1,
                      seed = "random", # default
                      nsim = 100, # faster
                      probs = c(0.025, 0.975)) # default


pred1$plotdata %>% head()

ggplot(data = pred1$plotdata, aes(x = ln_trade_lag_1, 
                                  y = mean,
                                  ymin = lower, ymax = upper)) +
  geom_ribbon(alpha = 0.1) + # Confidence intervals
  geom_line() + # Mean
  facet_wrap(.~ GlobSol, scales = "fixed", ncol = 2) +
  scale_y_continuous(labels = percent_format(accuracy = 1)) + # % labels
  scale_x_continuous(breaks = c(0,0.1,0.2,0.3,0.4,.5,0.6,0.8,0.9,1)) +
  theme_bw() +
  labs(y = "Predicted probabilities",
       x = "Trade") # Always label your axes ;)



pred1 <- mnl_pred_ova(model = mod1,
                      data = gles,
                      x = "nat_rents_lag_1",
                      by = 0.1,
                      seed = "random", # default
                      nsim = 100, # faster
                      probs = c(0.025, 0.975)) # default


pred1$plotdata %>% head()

ggplot(data = pred1$plotdata, aes(x = nat_rents_lag_1, 
                                  y = mean,
                                  ymin = lower, ymax = upper)) +
  geom_ribbon(alpha = 0.1) + # Confidence intervals
  geom_line() + # Mean
  facet_wrap(.~ GlobSol, scales = "fixed", ncol = 2) +
  scale_y_continuous(labels = percent_format(accuracy = 1)) + # % labels
  scale_x_continuous(breaks = c(0,0.1,0.2,0.3,0.4,.5,0.6,0.8,0.9,1)) +
  theme_bw() +
  labs(y = "Predicted probabilities",
       x = "NR") # Always label your axes ;)
```

```{r}

```




```{r}

# Load necessary packages
library(sandwich)    # For robust standard errors
library(lmtest)      # For hypothesis testing with robust standard errors
library(clubSandwich) # For clustered robust standard errors
# Full controls
Vars<-c(main_indip,econo,socio_poli,cof_deve)
# Create the complete formula
complete_formula <-gen_formula(dependent_var,Vars) 


# Fit the multinom model
multinom_model1 <- multinom(complete_formula, data = df_scaled, Hess = TRUE)

# Specify your clustering variable (e.g., "cluster_id")
cluster_var <- "iso3c"

# Get clustered robust standard errors using clubSandwich
clustered_vcov <- vcovCR(multinom_model1, cluster = df_scaled[[cluster_var]], type = "CR2")

# Test coefficients with robust clustered standard errors
robust_test <- coef_test(multinom_model1, vcov = clustered_vcov, test = "z")

# Display the results with robust clustered standard errors
print(robust_test)
```


## clustered se
```{r}

library(clusterSEs)

multinom_model4 <- multinom(complete_formula, data = df_scaled,
                            Hess = TRUE)

cluster.im.mlogit(
multinom_model4,
df_scaled,
~ iso3c,
ci.level = 0.95,
report = TRUE,
truncate = FALSE,
return.vcv = FALSE
)

```



## to see better later for robuustnes checks



## Run multinomial models
```{r}
# Define the dependent variable and set is as an unordered factors
dependent_var <- "GlobSol"
df_scaled$GlobSol <- factor(df_scaled$GlobSol)  # Ensure it's a factor
# Re-level the target variable to set 4 as the baseline
df_scaled$GlobSol <- relevel(df_scaled$GlobSol, ref = "4")


main_indip <- c("count_HO_lag_1", "trade_part_lag_1", "nat_rents_lag_1")
main_indip2 <- c("count_HO_lag_1", "trade_lag_1", "nat_rents_lag_1")
main_indip2 <- c("count_HO_lag_1", "FDI", "nat_rents_lag_1")


econo <- c("pop_tot_lag_1", "gdp_lag_1","inflation_lag_1","urb_pop_pct_lag_1")
socio_poli <- c("liberal_demo_lag_1", "military_centr_lag_1","regime_corruption_lag_1","civil_soc")
conflict<- c("OneSided_fat_lag_1", "NonState_conf_fat_lag_1","StateBased_conf_fat_lag_1")


# baseline model
Vars<-main_indip
# Create the complete formula
complete_formula <-gen_formula(dependent_var,Vars)
# Estimate the multinomial logistic regression model
multinom_model1 <- multinom(complete_formula, data = df_scaled)

# baseline model
Vars<-main_indip
# Create the complete formula
complete_formula <-gen_formula(dependent_var,Vars)
# Estimate the multinomial logistic regression model
multinom_model1 <- multinom(complete_formula, data = df_scaled)



```















```{r}
multinom_model5 <- multinom(GlobSol ~ count_HO_lag_1*trade_part_lag_1 + nat_rents_lag_1 + 
    pop_tot_lag_1 + gdp_lag_1 + inflation_lag_1 + urb_pop_pct_lag_1 + 
    liberal_demo_lag_1 + military_centr_lag_1 + regime_corruption_lag_1, data = df_scaled,
                            Hess = TRUE)
```


```{r}
# Create a comparison table with stargazer
stargazer(
  multinom_model5,
  type = "text",  # or "latex" or "html" for different output formats
  title = "Comparison of Multinomial Models",
  align = TRUE,
  no.space = TRUE,
  digits = 3,  # Number of decimal places to display
  column.labels = c("Model 5"),  # Label each model
  omit.stat = c("aic", "bic")  # Optionally omit some statistics for cleaner output
)
```








### plotting effects on predictions (old plots)
#### set function to plot
```{r}
# Define the plotting function
plot_predicted_probabilities <- function(plot_data, x_var) {
  # Ensure x_var is a string representing the x-axis variable
  if (!is.character(x_var)) {
    stop("x_var should be a character string representing the x-axis variable.")
  }
  
  # Create the ggplot object with the specified x_var
  ggplot(plot_data, aes_string(x = x_var)) +
    geom_line(aes_string(y = "`1`", color = "\"Category 1\"")) +  # Escaping quotes for static labels
    geom_line(aes_string(y = "`2`", color = "\"Category 2\"")) +
    geom_line(aes_string(y = "`3`", color = "\"Category 3\"")) +
    geom_line(aes_string(y = "`4`", color = "\"Category 4\"")) +
    labs(y = "Predicted Probability", x = x_var, color = "Category") +
    theme_minimal() +
    ggtitle(paste("Predicted Probabilities by", x_var))
}
```

#### plot marginal effects count ho
```{r}
df<-df_scaled
# Create a new data frame for prediction
# You can use sequences, random data, or actual data points for input
newdata <- data.frame(
  count_HO_lag_1 = seq(min(df$count_HO_lag_1), max(df$count_HO_lag_1), length.out = length(df$count_HO_lag_1)),
  trade_part_lag_1 = mean(df$trade_part_lag_1),
  nat_rents_lag_1 = mean(df$nat_rents_lag_1),
  pop_tot_lag_1 = mean(df$pop_tot_lag_1),
  gdp_lag_1 = mean(df$gdp_lag_1),
  inflation_lag_1 = mean(df$inflation_lag_1),
  urb_pop_pct_lag_1 = mean(df$urb_pop_pct_lag_1),
  liberal_demo_lag_1 = mean(df$liberal_demo_lag_1),
    military_centr_lag_1 = mean(df$military_centr_lag_1),
    regime_corruption_lag_1 = mean(df$regime_corruption_lag_1)
)

# Generate predicted probabilities for each category
predictions <- predict(multinom_model4, newdata, "probs")


# Create a data frame with predictions
plot_data <- cbind(newdata, predictions)
```

```{r}
# Plot using the defined function
plot_predicted_probabilities(plot_data, "count_HO_lag_1")
```

# plot marginal effects count trade
```{r}

df<-df_scaled
# Create a new data frame for prediction
# You can use sequences, random data, or actual data points for input
newdata <- data.frame(
  trade_part_lag_1 = seq(min(df$trade_part_lag_1), max(df$trade_part_lag_1), length.out = length(df$count_HO_lag_1)),
  count_HO_lag_1 = mean(df$count_HO_lag_1),
  nat_rents_lag_1 = mean(df$nat_rents_lag_1),
  pop_tot_lag_1 = mean(df$pop_tot_lag_1),
  gdp_lag_1 = mean(df$gdp_lag_1),
  inflation_lag_1 = mean(df$inflation_lag_1),
  urb_pop_pct_lag_1 = mean(df$urb_pop_pct_lag_1),
  liberal_demo_lag_1 = mean(df$liberal_demo_lag_1),
    military_centr_lag_1 = mean(df$military_centr_lag_1),
    regime_corruption_lag_1 = mean(df$regime_corruption_lag_1)
)

# Generate predicted probabilities for each category
predictions <- predict(multinom_model4, newdata, "probs")


# Create a data frame with predictions
plot_data <- cbind(newdata, predictions)

```

```{r}
# Plot using the defined function
plot_predicted_probabilities(plot_data, "trade_part_lag_1")
```

# plot marginal effects nat revs
```{r}

df<-df_scaled
# Create a new data frame for prediction
# You can use sequences, random data, or actual data points for input
newdata <- data.frame(
  nat_rents_lag_1 = seq(min(df$nat_rents_lag_1), max(df$nat_rents_lag_1), length.out = length(df$count_HO_lag_1)),
  count_HO_lag_1 = mean(df$count_HO_lag_1),
  trade_part_lag_1 = mean(df$trade_part_lag_1),
  pop_tot_lag_1 = mean(df$pop_tot_lag_1),
  gdp_lag_1 = mean(df$gdp_lag_1),
  inflation_lag_1 = mean(df$inflation_lag_1),
  urb_pop_pct_lag_1 = mean(df$urb_pop_pct_lag_1),
  liberal_demo_lag_1 = mean(df$liberal_demo_lag_1),
    military_centr_lag_1 = mean(df$military_centr_lag_1),
    regime_corruption_lag_1 = mean(df$regime_corruption_lag_1)
)

# Generate predicted probabilities for each category
predictions <- predict(multinom_model4, newdata, "probs")


# Create a data frame with predictions
plot_data <- cbind(newdata, predictions)
```

```{r}
# Plot using the defined function
plot_predicted_probabilities(plot_data, "nat_rents_lag_1")
```

## test what happen if we drop one category


## getting robust se
```{r}
# Install mlogit and AER packages and load them. Latter is just for a dataset we'll be using.
library("mlogit", "AER")

# Load dataset TravelMode
data("TravelMode", package = "AER")

# Use the mlogit() function to run a nested logit estimation

# Here, we will predict what mode of travel individuals
# choose using cost and wait times

nestedlogit = mlogit(
  choice ~ gcost + wait,
  data = TravelMode,
  ##The variable from which our nests are determined
  alt.var = 'mode',
  #The variable that dictates the binary choice
  choice = 'choice',
  #List of nests as named vectors
  nests = list(Fast = c('air','train'), Slow = c('car','bus'))
  )


# The results

summary(nestedlogit)
```


```{r}
nlm <- mlogit(
  choice ~ gcost + wait,
  data = TravelMode,
  nests = list(Fast = c('air','train'), Slow = c('car','bus'), reflevel = "car"))
summary(nlm)

```



```{r}
# Use stargazer to create a summary with custom standard errors
stargazer(
  multinom_model1,
  type = "text",
  se = list(bootstrap_se),
  title = "Multinomial Model with Robust Standard Errors",
  dep.var.labels = "GlobSol",
  covariate.labels = c("Count Ho Lag 1", "Trade Part Lag 1", "Nat Rents Lag 1"),
  out.header = TRUE
)
```


## Prepare for Nested logit
```{r}
# ## create choice variaböe
# data <- data.frame(
#   GlobSol_mode = c(1:4)
# )
# data$dummy<-1
# 
# 
# ## add dummy to main df
# df_scaled$dummy<-1
# 
# ## create reshaped dataset for nested model
# df_scaled_nested <- left_join(df_scaled, data, by = c("dummy" = "dummy"))
# 
# ## creatign outcome varible
# df_scaled_nested$GlobSol_outcome_text<-"no"
# df_scaled_nested$GlobSol_outcome_text<-ifelse(df_scaled_nested$GlobSol==df_scaled_nested$GlobSol_mode,"yes","no")
# 
# ## creatign outcome varible
# df_scaled_nested$GlobSol_outcome<-0
# df_scaled_nested$GlobSol_outcome<-ifelse(df_scaled_nested$GlobSol==df_scaled_nested$GlobSol_mode,1,0)
# 
# 
# 
# ## drop old useless variables
# df_scaled_nested <- df_scaled_nested[ , names(df_scaled_nested) %!in% c("GlobSol", "dummy")] 
# 
# 
# df_scaled_nested$GlobSol_mode_txt<-NA
# df_scaled_nested$GlobSol_mode_txt<-ifelse(df_scaled_nested$GlobSol_mode==1, "cosmo",df_scaled_nested$GlobSol_mode_txt)
# df_scaled_nested$GlobSol_mode_txt<-ifelse(df_scaled_nested$GlobSol_mode==2, "liberal",df_scaled_nested$GlobSol_mode_txt)
# df_scaled_nested$GlobSol_mode_txt<-ifelse(df_scaled_nested$GlobSol_mode==3, "colonial",df_scaled_nested$GlobSol_mode_txt)
# df_scaled_nested$GlobSol_mode_txt<-ifelse(df_scaled_nested$GlobSol_mode==4, "commu",df_scaled_nested$GlobSol_mode_txt)

```
## Export file
```{r}
#saving it
# namefile<-"df_full_nested.csv"
# folder_path_wb <- file.path(desktop_path, main_folder_name, sub_folder_name, namefile)
# write.csv(df_scaled_nested, folder_path_wb, row.names = FALSE)  # row.names = FALSE to exclude row indices

```









