---
title: "DatasetCompiler"
author: "MNB"
date: "2/15/2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## libraries
```{r}
library(Hmisc)
library(data.table)

library(R.utils)
library(plyr)
library(dplyr)
library(tidyverse)
library(tidyr)
library(naniar)
library(geosphere)
library(zoo)
library(stringr)
library(tidytext)
library(rworldmap)
library(gridExtra)


library(classInt)
library("ggplot2")
library(devtools)
library(DT)
library(dvmisc)
library(ggpubr)
library(gtools)
library(foreign)
library(GADMTools)
library(maps)


library(spdep)
library(lubridate)


library(WDI)
library(readxl)
library(haven)


library(reshape)

library(geojsonio)

library(countrycode)

library(roll)
```

# Remove lists 
```{r, include=FALSE}
## remove lists
rm(list=ls())
```

# Funtions 
```{r}
# more lines of code

# calcolate mode
mode <- function(v) {
  uniqv <- unique(v)
  uniqv[which.max(tabulate(match(v, uniqv)))]
}


# exclude
'%!in%' <- function(x,y)!('%in%'(x,y))

## drop NAs from column
Drop_NA <- function(dataset, col_name){
  col_name <- enquo(col_name)
  dataset %>%
    drop_na((!!col_name)) %>%
    as.data.frame()
}

## create 1 and 2 period lags (grouping by a variable)
Lag_12 <- function(dataset,col_name,x){
  {
    col_name <- enquo(col_name)
    dataset %>%
      group_by(!!col_name) %>%
      mutate(across(all_of(x),
                    .fns = ~ lag(.,1),
                    .names = paste0("{.col}_lag_",1)))%>%
      mutate(across(all_of(x),
                    .fns = ~ lag(.,2),
                    .names = paste0("{.col}_lag_",2)))
    
  } 
}

## create 1 and 2 period lags 
Lag_12_ngby <- function(dataset,x){
  {
    dataset %>%
      mutate(across(all_of(x),
                    .fns = ~ lag(.,1),
                    .names = paste0("{.col}_lag_",1)))%>%
      mutate(across(all_of(x),
                    .fns = ~ lag(.,2),
                    .names = paste0("{.col}_lag_",2)))
    
  } 
}

## assign 0 to NAs
Nas_to_0 <- function(dataset, x) {
  
  dataset %>% mutate_at(all_of(x), ~replace(., is.na(.), 0))
  
}


download_and_create_folder <- function(file_name, desktop_path, folder_name, url) {
  
  # Combine the desktop path with the folder name
  folder_path <- file.path(desktop_path,main_folder_name, folder_name)
  
  
  # Check if the folder exists
  if (!file.exists(folder_path)) {
    # If the folder doesn't exist, create it
    dir.create(folder_path)
    cat("Folder", folder_path, "created.\n")
  } else {
    # If the folder already exists, do nothing
    cat("Folder", folder_path, "already exists.\n")
  }
  
  # Specify the file path where you want to save the downloaded file
  file_path <- paste0(folder_path, "/", file_name)
  
  # Download the file
  download.file(url, file_path, mode = "wb")
}




download_create_folder_and_unzip <- function(desktop_path, folder_name, url) {
  
  # Combine the desktop path with the folder name
  folder_path <- file.path(desktop_path,main_folder_name, folder_name)
  
  
  # Check if the folder exists
  if (!file.exists(folder_path)) {
    # If the folder doesn't exist, create it
    dir.create(folder_path)
    cat("Folder", folder_path, "created.\n")
  } else {
    # If the folder already exists, do nothing
    cat("Folder", folder_path, "already exists.\n")
  }
  
  # Specify the file path where you want to save the downloaded file
  file_path <- folder_path
  
  # Download the file
  download.file(url, destfile = "temp.zip", mode = "wb")
  
  # Unzip the downloaded file
  unzip("temp.zip", exdir = file_path)
  
  # Delete the temporary zip file
  file.remove("temp.zip")
}

```


# Setting directory for datasets' folders
```{r}
desktop_path <- file.path("C:", "Users", "marco", "Desktop")
```


# Creating folder for datasets
```{r}
# Define the path to the desktop folder

# Define the name of the folder to check/create
main_folder_name <- "DFGlobalLab"

# Combine the desktop path with the folder name
folder_path <- file.path(desktop_path, main_folder_name)

# Check if the folder exists
if (!file.exists(folder_path)) {
  # If the folder doesn't exist, create it
  dir.create(folder_path)
  cat("Folder", main_folder_name, "created on the desktop.\n")
} else {
  # If the folder already exists, do nothing
  cat("Folder", main_folder_name, "already exists on the desktop.\n")
}
```

# Importing and reshaping Dfs

### Polity 2
#### Create folder and download
```{r}
sub_folder_name<-"polity2"
download_and_create_folder("p5v2018.xls",
                           desktop_path,
                           sub_folder_name,
                           "http://www.systemicpeace.org/inscr/p5v2018.xls")
```
#### Import
```{r}
file_path<-file.path(desktop_path,main_folder_name, sub_folder_name, "p5v2018.xls")
## import  dataset
Polity2<- read_excel(file_path)
```
# Create base
```{r}
## assign ISO3C
Polity2$iso3c <- countrycode(Polity2$country, "country.name", "iso3c")
## subset years of interests
Polity2<-subset(Polity2, Polity2$year>1988 & Polity2$year<2018)
## subset only columns of interest
df_Base<-Polity2[c("iso3c",
                "year")]


```

### ICEWS
#### link df
#### Importing ICEWS
```{r}


```

#### Reshaping ICEWS
```{r}

```


### EMDAT
#### link df: https://www.emdat.be/database (for EMdat there is no API and a format to download. thus I sugest to manually create a subfolder named EMDAT in the folder DFGlobalLab and save there the EMdat dataset manually downloaded from here: https://public.emdat.be/data. on February 17th I downloaded the dataset selecting both natural and technological disasters in the form "classification", and selecting all the continets in the from "countries". For the time period I selected 1980 - 2020. I transofremd the file in a STATA dataset and uploaded the file on github under the name emdat) 
#### Importing EMDAT
```{r}
sub_folder_name<-"EMDAT"
URL_df<-file.path(desktop_path,main_folder_name, sub_folder_name, "emdat.dta")
## import  dataset
EMDAT<- haven::read_dta(URL_df)
```

#### Reshaping EMDAT
```{r}
EM_dat<-EMDAT
##subset years
EM_dat<-subset(EM_dat, EM_dat$StartYear>=1980)

#select variables of interests
EM_dat<-EM_dat[c("DisNo",
                 "StartYear",
                 "EndYear",
                 "StartMonth",
                 "EndMonth",
                 "DisasterGroup",
                 "DisasterSubgroup",
                 "DisasterType",
                 "DisasterSubtype",
                 "ISO",
                 "Country")]

#rename variables
names(EM_dat)[names(EM_dat) == "Year"] <- "year"
names(EM_dat)[names(EM_dat) == "Country"] <- "country_Emdat"

#drop events without date
EM_dat<-EM_dat[!(is.na(EM_dat$`StartMonth`)),]
EM_dat<-EM_dat[!(is.na(EM_dat$`EndMonth`)),]

#create  dates event and start datasets
EM_dat$Date.start <- paste0(EM_dat$`StartYear`,
                            "-",
                            EM_dat$`StartMonth`)

EM_dat$Date.start<-as.yearmon(EM_dat$Date.start)


EM_dat$Date.end <- paste0(EM_dat$`EndYear`,
                            "-",
                            EM_dat$`EndMonth`)

EM_dat$Date.end<-as.yearmon(EM_dat$Date.end)

#as date
EM_dat$Date.start<-as.Date(EM_dat$Date.start)
EM_dat$Date.end<-as.Date(EM_dat$Date.end)

#rename countries
EM_dat$country_Emdat[EM_dat$country_Emdat=="Czechoslovakia"] <- "Czech Republic (the)"
EM_dat$country_Emdat[EM_dat$country_Emdat=="Germany Fed Rep"] <- "Germany"
EM_dat$country_Emdat[EM_dat$country_Emdat=="Korea (the Republic of)"] <- "Korea South"
EM_dat$country_Emdat[EM_dat$country_Emdat=="Korea (the Democratic People's Republic of)"] <- "Korea North"
EM_dat$country_Emdat[EM_dat$country_Emdat=="Germany Fed Rep"] <- "Germany"
EM_dat$country_Emdat[EM_dat$country_Emdat=="Serbia Montenegro"] <- "Serbia"
EM_dat$country_Emdat[EM_dat$country_Emdat=="Yugoslavia"] <- "Serbia"

#create iso3c
EM_dat$iso3c <- countrycode(EM_dat$country_Emdat, "country.name", "iso3c")

#drop iso3c NAs
EM_dat<-EM_dat[!is.na(EM_dat$iso3c), ]


#subset variables
EM_dat<-EM_dat[c("DisNo",
                 "iso3c",
                 "DisasterSubgroup",
                 "Date.start",
                 "Date.end")]
#sort dataset
EM_dat<-EM_dat[
  with(EM_dat, order(iso3c, Date.start)),
]


#reshape dataset
EM_dat<-EM_dat %>%
  group_by(iso3c, `DisNo`, `DisasterSubgroup`) %>%
  summarise(date = list(seq(floor_date(min(Date.start),unit = "month"),
                            floor_date(max(Date.end), unit = "month"),
                            by = "month"))) %>%
  tidyr::unnest(cols = c(date))

#sort dataframe
EM_dat<-EM_dat[
  with(EM_dat, order(iso3c, date)),
]

#create dummy for  count
EM_dat$count<-1

# count events
EM_dat<- EM_dat %>%
  group_by(iso3c, `DisasterSubgroup`, date ) %>%
  summarize(count = sum(count))

#reshape
EM_dat<-reshape2::dcast(EM_dat, date+iso3c~`DisasterSubgroup`)


## create date vector for EMDAT
Date<-as.data.frame(seq(as.Date("1960-1-1"), as.Date("2018-12-31"), by = "month"))
names(Date)[1] <- "Date.month"
Date$Dummy<-1
Date$Date.month<-as.yearmon(Date$Date.month)

#merge with CY date
#vector countries
EM_dat_C<-as.data.frame(unique(EM_dat$iso3c))
names(EM_dat_C)[1] <- "iso3c"
EM_dat_C$Dummy<-1
#assign dates
EM_dat_CY<-left_join(EM_dat_C, Date)

#merge with vector dates countries
EM_dat$Date.month<-as.yearmon(EM_dat$date)
EM_dat= left_join(EM_dat_CY, EM_dat, by = c("Date.month" = "Date.month", "iso3c" = "iso3c"))

#correct names
EM_dat<-janitor::clean_names(EM_dat)

#list variables MDat
List<- colnames(EM_dat)[!colnames(EM_dat) %in% c("iso3c", "dummy", "date_month", "date")]

# assign 0s
EM_dat<-Nas_to_0(EM_dat,List)

## drop date
EM_dat <- EM_dat[ , ! names(EM_dat) %in% c("date")]

#create variable year
EM_dat$year<-as.double((substr(( c(EM_dat$date_month)), 5, 9)))

## collapse to the counry-year level. for eacou country count the numbet of month experiencing the generic disaster D
EM_dat_y<- EM_dat %>% 
  group_by(iso3c, year ) %>%
  summarize(ext_ter_n_m = sum(extra_terrestrial),
            geo_n_m = sum(geophysical),
            hydro_n_m = sum(hydrological),
            indu_n_m = sum(industrial_accident),
            meteo_n_m = sum(meteorological),
            misc_n_m = sum(miscellaneous_accident),
            transport_n_m = sum(transport),
            bio_n_m = sum(biological),
            climat_n_m = sum(climatological))



## merge with Base
EM_dat_y= left_join(df_Base, EM_dat_y, by = c("year" = "year", "iso3c" = "iso3c"))

#list variables MDat
List<- colnames(EM_dat_y)[!colnames(EM_dat_y) %in% c("iso3c", "year")]

# assign 0s
EM_dat_y<-Nas_to_0(EM_dat_y,List)

# Lag 12
EM_dat_y <-Lag_12(EM_dat_y,iso3c, List)

# correct names
EM_dat_y<-janitor::clean_names(EM_dat_y)

```


### AidData
#### link df: https://www.aiddata.org/data/aiddata-core-research-release-level-1-v3-0#### Create folder and download
#### Create folder and download
```{r}
sub_folder_name<-"Aidata"
download_create_folder_and_unzip(desktop_path,
                           sub_folder_name,
                           "https://github.com/AidData-WM/public_datasets/releases/download/v3.0/AidDataCore_ResearchRelease_Level1_v3.0.zip")
```

#### Import
```{r}
file_path<-file.path(desktop_path,main_folder_name, sub_folder_name, "AidDataCoreDonorRecipientYearPurpose_ResearchRelease_Level1_v3.0.csv")
## import  dataset
Aiddata<- read.csv(file_path)
```


#### Reshaping AidData - calculating total amount of aid
```{r}
df_Aiddata<-Aiddata

## aggregate at country recipient level
df_Aiddata<- df_Aiddata %>% 
  group_by(recipient, year ) %>%
  summarize(AidData_tot_commit = sum(commitment_amount_usd_constant_sum))

#change names
df_Aiddata$recipient[df_Aiddata$recipient=="Yugoslavia"] <- "Serbia"
df_Aiddata$recipient[df_Aiddata$recipient=="Serbia and Montenegro"] <- "Serbia"
df_Aiddata$recipient[df_Aiddata$recipient=="Soviet Union"] <- "Russia"

#assign ISO3
df_Aiddata$iso3c <- countrycode(df_Aiddata$recipient, "country.name", "iso3c")

#drop iso3c NAs
df_Aiddata<-df_Aiddata[!is.na(df_Aiddata$iso3c), ]

#create Aiddata country date dataset
df_Aiddata_C<-as.data.frame(unique(df_Aiddata$iso3c))
names(df_Aiddata_C)[1] <- "iso3c"
df_Aiddata_C$Dummy<-1
Date_Y_AidData<-as.data.frame(seq(as.Date("1970-1-1"), as.Date("2013-12-31"), by = "year"))
names(Date_Y_AidData)[1] <- "year"
Date_Y_AidData$Dummy<-1
Date_Y_AidData$year<-as.double((substr(( c(Date_Y_AidData$year)), 1, 4)))
df_Aiddata_CY<-left_join(df_Aiddata_C,Date_Y_AidData)

# merge with with aid data country year vector
df_Aiddata<-left_join(df_Aiddata_CY,df_Aiddata, by = c("iso3c" = "iso3c","year"="year"))

#drop duplicates (usual yuogoslavia and soviet union "problem" with name change to serbia and russia)
df_Aiddata<-df_Aiddata %>% 
                distinct(year, iso3c , .keep_all = TRUE)

## merge with world Bank Population
WorldBank_pop <- WDI(
  country = "all",
  indicator = c("Pop_tot"="SP.POP.TOTL"),
  start = 1960,
  end = 2020,
  extra = TRUE,
  cache = NULL,
  latest = NULL,
  language = "en"
)

## assign ISO3
names(WorldBank_pop)[names(WorldBank_pop) == "country"] <- "country_wb"
WorldBank_pop$iso3c <- countrycode(WorldBank_pop$country_wb, "country.name", "iso3c")

# merge with aid data 
df_Aiddata<-left_join(df_Aiddata,WorldBank_pop)

##assign 0s and NAs
List<-c("AidData_tot_commit")
df_Aiddata<-Nas_to_0(df_Aiddata, List)

#divide by population
df_Aiddata$AidData_tot_commit_per_cap<-df_Aiddata$AidData_tot_commit/df_Aiddata$Pop_tot

# keep var of interest
df_Aiddata <- df_Aiddata[ , !names(df_Aiddata) %in% c("Dummy",
                                                      "iso2c",
                                                      "country_wb",
                                                      "Pop_tot",
                                                      "region",
                                                      "capital",
                                                      "longitude",
                                                      "latitude",
                                                      "income",
                                                      "lending")]
## merge with Base
df_Aiddata= left_join(df_Base, df_Aiddata, by = c("year" = "year", "iso3c" = "iso3c"))

#list variables MDat
List<- colnames(df_Aiddata)[!colnames(df_Aiddata) %in% c("iso3c", "year")]

# assign 0s
df_Aiddata<-Nas_to_0(df_Aiddata,List)

```

#### Reshaping AidData - calculating total amount of aid by sector
```{r}
#load dataset
df_Aiddata_sectoral<-Aiddata

#create schort code
df_Aiddata_sectoral$Short_code<-c((substr(( c(df_Aiddata_sectoral$coalesced_purpose_code)), 1, 2)))

## rename codes
df_Aiddata_sectoral$Short_code[df_Aiddata_sectoral$Short_code=="10"] <- "Social_Infra"
df_Aiddata_sectoral$Short_code[df_Aiddata_sectoral$Short_code=="11"] <- "Education"
df_Aiddata_sectoral$Short_code[df_Aiddata_sectoral$Short_code=="12"] <- "Health"
df_Aiddata_sectoral$Short_code[df_Aiddata_sectoral$Short_code=="13"] <- "Population_Policies"
df_Aiddata_sectoral$Short_code[df_Aiddata_sectoral$Short_code=="14"] <- "Water_Supply_Sanitation"
df_Aiddata_sectoral$Short_code[df_Aiddata_sectoral$Short_code=="15"] <- "Gov_Civ_Soc"
df_Aiddata_sectoral$Short_code[df_Aiddata_sectoral$Short_code=="16"] <- "Soc_Infra"
df_Aiddata_sectoral$Short_code[df_Aiddata_sectoral$Short_code=="20"] <- "Eco_Infra"
df_Aiddata_sectoral$Short_code[df_Aiddata_sectoral$Short_code=="21"] <- "Trans_Stor"
df_Aiddata_sectoral$Short_code[df_Aiddata_sectoral$Short_code=="22"] <- "Comm"
df_Aiddata_sectoral$Short_code[df_Aiddata_sectoral$Short_code=="23"] <- "Energy_Gen_Supp"
df_Aiddata_sectoral$Short_code[df_Aiddata_sectoral$Short_code=="24"] <- "Banking"
df_Aiddata_sectoral$Short_code[df_Aiddata_sectoral$Short_code=="25"] <- "Business"
df_Aiddata_sectoral$Short_code[df_Aiddata_sectoral$Short_code=="30"] <- "Production Sectors"
df_Aiddata_sectoral$Short_code[df_Aiddata_sectoral$Short_code=="31"] <- "Agri_For_Fish"
df_Aiddata_sectoral$Short_code[df_Aiddata_sectoral$Short_code=="32"] <- "Ind_Min_Cons"
df_Aiddata_sectoral$Short_code[df_Aiddata_sectoral$Short_code=="33"] <- "Trade_policy "
df_Aiddata_sectoral$Short_code[df_Aiddata_sectoral$Short_code=="41"] <- "Env_Protection"
df_Aiddata_sectoral$Short_code[df_Aiddata_sectoral$Short_code=="42"] <- "Women"
df_Aiddata_sectoral$Short_code[df_Aiddata_sectoral$Short_code=="43"] <- "Other"
df_Aiddata_sectoral$Short_code[df_Aiddata_sectoral$Short_code=="51"] <- "Budget_Support"
df_Aiddata_sectoral$Short_code[df_Aiddata_sectoral$Short_code=="52"] <- "Food_Security"
df_Aiddata_sectoral$Short_code[df_Aiddata_sectoral$Short_code=="53"] <- "Commodity_Assistance"
df_Aiddata_sectoral$Short_code[df_Aiddata_sectoral$Short_code=="60"] <- "Debt"
df_Aiddata_sectoral$Short_code[df_Aiddata_sectoral$Short_code=="70"] <- "Humanitarian_Aid"
df_Aiddata_sectoral$Short_code[df_Aiddata_sectoral$Short_code=="72"] <- "Emergency_Response"
df_Aiddata_sectoral$Short_code[df_Aiddata_sectoral$Short_code=="73"] <- "Reconstruction_Relief"
df_Aiddata_sectoral$Short_code[df_Aiddata_sectoral$Short_code=="74"] <- "Disaster_Prevention"
df_Aiddata_sectoral$Short_code[df_Aiddata_sectoral$Short_code=="91"] <- "Administrative_costs"
df_Aiddata_sectoral$Short_code[df_Aiddata_sectoral$Short_code=="92"] <- "Support_NGO"
df_Aiddata_sectoral$Short_code[df_Aiddata_sectoral$Short_code=="93"] <- "Refugees_Donor"
df_Aiddata_sectoral$Short_code[df_Aiddata_sectoral$Short_code=="99"] <- "Unallocated"


#change names countries
df_Aiddata_sectoral$recipient[df_Aiddata_sectoral$recipient=="Yugoslavia"] <- "Serbia"
df_Aiddata_sectoral$recipient[df_Aiddata_sectoral$recipient=="Serbia and Montenegro"] <- "Serbia"
df_Aiddata$recipient[df_Aiddata$recipient=="Soviet Union"] <- "Russia"

#assign ISO3
df_Aiddata_sectoral$iso3c <- countrycode(df_Aiddata_sectoral$recipient, "country.name", "iso3c")

#drop iso3c NAs
df_Aiddata_sectoral<-df_Aiddata_sectoral[!is.na(df_Aiddata_sectoral$iso3c), ]

## aggregate at country recipient purpose level
df_Aiddata_sectoral<- df_Aiddata_sectoral %>% 
  group_by(iso3c, year,Short_code ) %>%
  summarize(commitment_tot = sum(commitment_amount_usd_constant_sum))

# merge with with aid data country year vector
df_Aiddata_sectoral<-left_join(df_Aiddata_CY,df_Aiddata_sectoral, by = c("iso3c" = "iso3c","year"="year"))

## merge with wb
df_Aiddata_sectoral<-left_join(df_Aiddata_sectoral,WorldBank_pop, by = c("iso3c" = "iso3c","year"="year"))

#divide by population
df_Aiddata_sectoral$commit_per_cap<-df_Aiddata_sectoral$commitment_tot/df_Aiddata_sectoral$Pop_tot

# keep var of interest
df_Aiddata_sectoral <- df_Aiddata_sectoral[ ,  names(df_Aiddata_sectoral) %in% c("iso3c",
                                                                                  "year",
                                                                                  "Short_code",
                                                                                  "commit_per_cap",
                                                                                  "commitment_tot")]

#reshape
dcast1 <- reshape2::dcast(df_Aiddata_sectoral, iso3c + year ~ Short_code, value.var="commit_per_cap")
dcast2 <- reshape2::dcast(df_Aiddata_sectoral, iso3c + year ~ Short_code, value.var="commitment_tot")

#rename vars
cols_to_rename <- names(dcast1)[!(names(dcast1) %in% c("year", "iso3c"))]
dcast1 <- dcast1 %>%
  rename_with(~ paste0(., "_pc"), cols_to_rename)
dcast2 <- dcast2 %>%
  rename_with(~ paste0(., "_tot"), cols_to_rename)

# merge with dcast1 and dcast2 with aid data country year vector
df_Aiddata_sectoral<-left_join(df_Aiddata_CY, dcast1, by = c("iso3c" = "iso3c","year"="year"))
df_Aiddata_sectoral<-left_join(df_Aiddata_sectoral, dcast2, by = c("iso3c" = "iso3c","year"="year"))


#assign 0s
df_Aiddata_sectoral[is.na(df_Aiddata_sectoral)] = 0


#drop duplicates
df_Aiddata_sectoral<-df_Aiddata_sectoral %>% 
                distinct(year, iso3c , .keep_all = TRUE)

## merge with Base
df_Aiddata= left_join(df_Base, df_Aiddata, by = c("year" = "year", "iso3c" = "iso3c"))

#list variables MDat
List<- colnames(df_Aiddata)[!colnames(df_Aiddata) %in% c("iso3c", "year")]

# assign 0s
df_Aiddata<-Nas_to_0(df_Aiddata,List)

```


### UCDP GED
#### link df: https://ucdp.uu.se/downloads/index.html#ged_global
#### Create folder and download
```{r}
sub_folder_name<-"UCDP"
download_create_folder_and_unzip(desktop_path,
                           sub_folder_name,
                           "https://ucdp.uu.se/downloads/ged/ged231-csv.zip")
```

#### Import
```{r}
file_path<-file.path(desktop_path,main_folder_name, sub_folder_name, "GEDEvent_v23_1.csv")
## import  dataset
UCDP_GED<- read.csv(file_path)
```


#### Reshaping UCDP GED
```{r}
df_UCDP_GED<-UCDP_GED

#assign ISO3
df_UCDP_GED$iso3c <- countrycode(df_UCDP_GED$country, "country.name", "iso3c")


## aggregate at country iso3c level
df_UCDP_GED<- df_UCDP_GED %>% 
  group_by(iso3c, year, type_of_violence) %>%
  summarize(n_fatalities = sum(best))

#reshape
df_UCDP_GED<-reshape2::dcast(df_UCDP_GED, year+iso3c~`type_of_violence`)

## merge with Base
df_UCDP_GED= left_join(df_Base, df_UCDP_GED, by = c("year" = "year", "iso3c" = "iso3c"))

#list variables ged
List<- colnames(df_UCDP_GED)[!colnames(df_UCDP_GED) %in% c("iso3c", "year")]

# assign 0s
df_UCDP_GED<-Nas_to_0(df_UCDP_GED,List)

#rename variables
names(df_UCDP_GED)[names(df_UCDP_GED) == "1"] <- "StateBased_conf_fat"
names(df_UCDP_GED)[names(df_UCDP_GED) == "2"] <- "NonState_conf_fat"
names(df_UCDP_GED)[names(df_UCDP_GED) == "3"] <- "OneSided_fat"


```


### ESD
#### link df https://ucdp.uu.se/downloads/index.html#externalsupport
#### Create folder and download
```{r}
sub_folder_name<-"UCDP"
download_create_folder_and_unzip(desktop_path,
                           sub_folder_name,
                           "https://ucdp.uu.se/downloads/ged/ged231-csv.zip")
```

#### Import
```{r}
file_path<-file.path(desktop_path,main_folder_name, sub_folder_name, "GEDEvent_v23_1.csv")
## import  dataset
UCDP_GED<- read.csv(file_path)
```

#### Reshaping ESD
```{r}

```


## Merge datasets
```{r}

```

## export final df
```{r}

```

