---
title: "Untitled"
author: "MNB"
date: "12/9/2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 09 12 2024
# Restart R
```{r}
.rs.restartR()
```


## Libraries
```{r, include=FALSE}
library(Hmisc)
library(data.table)

library(R.utils)
library(tidyverse)
library(naniar)
library(zoo)


library(classInt)
#library(devtools)
library(DT)
library(dvmisc)
#library(ggpubr)
library(gtools)
library(foreign)

library(lubridate)

library(readxl)
library(haven)
library(jsonlite)


library(reshape)

library(countrycode)

library(roll)
```

# Remove lists 
```{r, include=FALSE}
## remove lists
rm(list=ls())
```

# Funtions 
```{r, include=FALSE}

# exclude
'%!in%' <- function(x,y)!('%in%'(x,y))

drop_columns <- function(data, columns_to_drop) {
  data <- data[, names(data) %!in% columns_to_drop, drop = FALSE]
  return(data)
}


## drop NAs from column
Drop_NA <- function(dataset, col_name){
  col_name <- enquo(col_name)
  dataset %>%
    drop_na((!!col_name)) %>%
    as.data.frame()
}

## create 1 and 2 period lags (grouping by a variable)
Lag_12 <- function(dataset,col_name,x){
  {
    col_name <- enquo(col_name)
    dataset %>%
      group_by(!!col_name) %>%
      mutate(across(all_of(x),
                    .fns = ~ lag(.,1),
                    .names = paste0("{.col}_lag_",1)))%>%
      mutate(across(all_of(x),
                    .fns = ~ lag(.,2),
                    .names = paste0("{.col}_lag_",2)))
    
  } 
}

## create 1 and 2 period lags 
Lag_12_ngby <- function(dataset,x){
  {
    dataset %>%
      mutate(across(all_of(x),
                    .fns = ~ lag(.,1),
                    .names = paste0("{.col}_lag_",1)))%>%
      mutate(across(all_of(x),
                    .fns = ~ lag(.,2),
                    .names = paste0("{.col}_lag_",2)))
    
  } 
}

## assign 0 to NAs
Nas_to_0 <- function(dataset, x) {
  
  dataset %>% mutate_at(all_of(x), ~replace(., is.na(.), 0))
  
}


download_and_create_folder <- function(file_name, desktop_path, folder_name, url) {
  
  # Combine the desktop path with the folder name
  folder_path <- file.path(desktop_path,main_folder_name, folder_name)
  
  
  # Check if the folder exists
  if (!file.exists(folder_path)) {
    # If the folder doesn't exist, create it
    dir.create(folder_path)
    cat("Folder", folder_path, "created.\n")
  } else {
    # If the folder already exists, do nothing
    cat("Folder", folder_path, "already exists.\n")
  }
  
  # Specify the file path where you want to save the downloaded file
  file_path <- paste0(folder_path, "/", file_name)
  
  # Download the file
  download.file(url, file_path, mode = "wb")
}




download_create_folder_and_unzip <- function(desktop_path, folder_name, url) {
  
  # Combine the desktop path with the folder name
  folder_path <- file.path(desktop_path,main_folder_name, folder_name)
  
  
  # Check if the folder exists
  if (!file.exists(folder_path)) {
    # If the folder doesn't exist, create it
    dir.create(folder_path)
    cat("Folder", folder_path, "created.\n")
  } else {
    # If the folder already exists, do nothing
    cat("Folder", folder_path, "already exists.\n")
  }
  
  # Specify the file path where you want to save the downloaded file
  file_path <- folder_path
  
  # Download the file
  download.file(url, destfile = "temp.zip", mode = "wb")
  
  # Unzip the downloaded file
  unzip("temp.zip", exdir = file_path)
  
  # Delete the temporary zip file
  file.remove("temp.zip")
}


# Define a function to rename specified columns with a given suffix
rename_columns <- function(df, suffix, vars_to_change) {
  # Create new names for the specified variables by adding the suffix
  new_names <- setNames(paste0(vars_to_change, suffix), vars_to_change)
  
  # Rename the columns in the data frame
  names(df)[names(df) %in% names(new_names)] <- new_names[names(df)[names(df) %in% names(new_names)]]
  
  # Return the modified data frame
  return(df)
}
```

# Setting directory for datasets' folders
```{r}
desktop_path <- file.path("C:", "Users", "marco", "Desktop")
#desktop_path <- file.path("C:", "Users","krogers","Documents")
```

# Set main folder name
```{r}
# Define the name of the folder to check/create
main_folder_name <- "DFGlobalLab"
#main_folder_name <- "data"
```

# Creating folder for datasets
```{r}

# Combine the desktop path with the folder name
folder_path <- file.path(desktop_path, main_folder_name)

# Check if the folder exists
if (!file.exists(folder_path)) {
  # If the folder doesn't exist, create it
  dir.create(folder_path)
  cat("Folder", main_folder_name, "created on the desktop.\n")
} else {
  # If the folder already exists, do nothing
  cat("Folder", main_folder_name, "already exists on the desktop.\n")
}
```

# Importing and reshaping Dfs

## Polity 2
#### Set subfolder name
```{r}
sub_folder_name<-"polity2"
```

#### Create folder and download
```{r}
# download_and_create_folder("p5v2018.xls",
#                            desktop_path,
#                            sub_folder_name,
#                            "http://www.systemicpeace.org/inscr/p5v2018.xls")
```

#### Import
```{r}
file_path<-file.path(desktop_path,main_folder_name, sub_folder_name, "p5v2018.xls")
## import  dataset
Polity2<- read_excel(file_path)
```

# Create bases - at year and month levels
```{r}
df_Polity2<-Polity2

# Create base at year level
## subset years of interests
df_Polity2<-subset(df_Polity2, df_Polity2$year>1970 & Polity2$year<2020)

# Rename countries
  replacements <- c(
    "Czechoslovakia"    = "Czech Republic (the)",
    "Serbia Montenegro" = "Serbia",
    "Yugoslavia"        = "Serbia"
  )
  df_Polity2$country <- ifelse(df_Polity2$country %in% names(replacements), replacements[df_Polity2$country], df_Polity2$country)

## assign ISO3C
df_Polity2$iso3c <- countrycode(df_Polity2$country, "country.name", "iso3c")

## subset only columns of interest
df_Base_Y<-df_Polity2[c("country",
                        "iso3c",
                        "year")]

# Complete panel
df_Base_Y<-df_Base_Y %>%
  complete(iso3c,year=c(1971:2021)) %>%
  group_by(iso3c) %>% fill(country) %>%
  ungroup()

## drop iso3c NA
df_Base_Y<-Drop_NA(df_Base_Y, iso3c)

#drop duplicates (usual yuogoslavia and soviet union "problem" with name change to serbia and russia)
df_Base_Y<-df_Base_Y %>% 
                distinct(year, iso3c , .keep_all = TRUE)

## correct names
df_Base_Y<-janitor::clean_names(df_Base_Y)

# Create base at month level
## set list of countries
Countries<-as.data.frame(unique(df_Base_Y$country))
names(Countries)[1] <- "country"
Countries$Dummy<-1
## assign ISO3C
Countries$iso3c <- countrycode(Countries$country, "country.name", "iso3c")
## set list of months
Date<-as.data.frame(seq(as.Date("1980-1-1"), as.Date("2021-12-31"), by = "month"))
names(Date)[1] <- "Date.month"
Date$Dummy<-1
Date$Date.month<-as.yearmon(Date$Date.month)
## create base
df_Base_YM<-left_join(Countries,Date)
## drop dummy
List<-c("Dummy")
df_Base_YM<-drop_columns(df_Base_YM,List)
## create year variable
df_Base_YM$year <- as.integer(c((substr(( c(df_Base_YM$Date.month)), 5, 8))))

## correct names
df_Base_YM<-janitor::clean_names(df_Base_YM)

```

## Diego Puga colonial heritage
## https://diegopuga.org/data/rugged/
### Set name folder
```{r}
sub_folder_name<-"Roughness"
```
### download dataset
```{r}

 # download_create_folder_and_unzip(desktop_path,
 #                            sub_folder_name,
 #                           "https://diegopuga.org/data/rugged/rugged_data.zip")

```

### Import
```{r}
file_path<-file.path(desktop_path,main_folder_name, sub_folder_name, "rugged_data.csv")
## import  dataset
df_rugged<- read.csv(file_path)
```

### process
```{r}
#change names
df_rugged$country[df_rugged$country=="Yugoslavia"]            <- "Serbia"
df_rugged$country[df_rugged$country=="Serbia and Montenegro"] <- "Serbia"

#assign ISO3
df_rugged$iso3c <- countrycode(df_rugged$country, "country.name", "iso3c")

#drop iso3c NAs
df_rugged<-df_rugged[!is.na(df_rugged$iso3c), ]
```

## Temperatures
```{r}
# Fetch the data
temperatures       <- read.csv("https://ourworldindata.org/grapher/monthly-temperature-anomalies.csv?v=1&csvType=full&useColumnShortNames=true")
df_temperatures    <-temperatures

#create year var
df_temperatures$year  <- c((substr(( c(df_temperatures$Day)), 1, 4)))

## assign iso3c
df_temperatures$iso3c <- countrycode(df_temperatures$Entity, "country.name", "iso3c")

## drop if iso3c is NA
df_temperatures       <-Drop_NA(df_temperatures, iso3c)

# keep vars of interest
df_temperatures       <- df_temperatures[c("iso3c",
                                            "year",
                                            "temperature_anomaly")]


## aggregate at country iso3c level
df_temperatures <- df_temperatures %>%
  group_by(iso3c, year) %>%
   dplyr::summarize(temp_anom = mean(temperature_anomaly, na.rm = TRUE))


# assign 0s to NAs
List<-c("temp_anom")
# create lags
df_temperatures <- Lag_12(df_temperatures, iso3c, List)

## correct names
df_temperatures<-janitor::clean_names(df_temperatures)

```

## Precipitations
```{r}
# Fetch the data
precipitation             <- read.csv("https://ourworldindata.org/grapher/average-precipitation-per-year.csv?v=1&csvType=full&useColumnShortNames=true")
df_precipitation          <-precipitation

## assign iso3c
df_precipitation$iso3c     <- countrycode(df_precipitation$Entity, "country.name", "iso3c")

df_precipitation$prep_yrl <-df_precipitation$total_precipitation

# keep vars of interest
df_precipitation           <- df_precipitation[c("iso3c",
                                               "Year",
                                               "prep_yrl")]

# assign 0s to NAs
List<-c("prep_yrl")
# create lags
df_precipitation <- Lag_12(df_precipitation, iso3c, List)

## correct names
df_precipitation<-janitor::clean_names(df_precipitation)

```



## EMDAT data on disasters in the country
#### Set subfolder name
```{r}
sub_folder_name<-"EMDAT"
```

#### Importing dataset
```{r}
file_path<-file.path(desktop_path,main_folder_name, sub_folder_name, "emdat.dta")
## import  dataset
EMDAT<- haven::read_dta(file_path)
```


```{r}

# Function to process dataset
process_EmDat_1 <- function(data) {
  # Subset years
  data <- subset(data, StartYear >= 1970)
  
  # Drop technological disasters
  data <- subset(data, DisasterGroup == "Natural")
  
  # Select variables of interest
  data <- data[c("DisNo",
                 "StartYear",
                 "EndYear",
                 "StartMonth",
                 "EndMonth",
                 "DisasterGroup",
                 "DisasterSubgroup",
                 "DisasterType",
                 "DisasterSubtype",
                 "ISO",
                 "Country")]
  
  # Rename variables
  names(data)[names(data) == "Year"]    <- "year"
  names(data)[names(data) == "Country"] <- "country_Emdat"
  
  # Drop events without date
  data <- data[complete.cases(data$StartMonth, data$EndMonth), ]
  
  # Create date variables
  data$Date.start <- as.Date(paste0(data$StartYear, "-", data$StartMonth, "-01"))
  data$Date.end <- as.Date(paste0(data$EndYear, "-", data$EndMonth, "-01"))
  
  # Rename countries
  replacements <- c(
    "Czechoslovakia"                              = "Czech Republic (the)",
    "Germany Fed Rep"                             = "Germany",
    "Korea (the Republic of)"                     = "Korea South",
    "Korea (the Democratic People's Republic of)" = "Korea North",
    "Serbia Montenegro"                           = "Serbia",
    "Yugoslavia"                                  = "Serbia"
  )
  data$country_Emdat <- ifelse(data$country_Emdat %in% names(replacements), replacements[data$country_Emdat], data$country_Emdat)
  
  # Create ISO codes
  data$iso3c <- countrycode(data$country_Emdat, "country.name", "iso3c")
  
  # Drop NA ISO codes
  data <- data[complete.cases(data$iso3c), ]
  
  # Subset variables
  data <- data[c("DisNo", "iso3c", "DisasterSubgroup", "Date.start", "Date.end")]
  
  # Sort dataset
  data <- data[order(data$iso3c, data$Date.start), ]
  
  return(data)
}

# Apply function 
EM_dat <- process_EmDat_1(EMDAT )

  
  
```

#### Getting it in a country-year-month panel format
```{r}

process_EmDat_2 <- function(df, df_basey) {
# Reshape dataset
df <- df %>%
  group_by(iso3c, DisNo, DisasterSubgroup) %>%
  summarise(date = list(seq(floor_date(min(Date.start), unit = "month"),
                            floor_date(max(Date.end), unit = "month"),
                            by = "month"))) %>%
  unnest(cols = c(date))

# Sort dataframe
df <- df[order(df$iso3c, df$date), ]

# Create dummy for count
df$count <- 1

# Count events
df <- df %>%
  group_by(iso3c, DisasterSubgroup, date) %>%
  summarise(count = sum(count))

# Reshape
df <- dcast(df, date + iso3c ~ DisasterSubgroup)

# Merge with vector dates countries
df$Date_month <- as.yearmon(df$date)
df <- left_join(df_basey, df, by = c("date_month" = "Date_month", "iso3c" = "iso3c"))

# List variables
List <- setdiff(names(df), c("country", "year", "iso3c", "count", "date_month", "date"))

# Assign 0s
df <- df %>%
  mutate(across(all_of(List), ~ replace_na(., 0)))

# Drop date
df <- dplyr::select(df, -date)

# Create variable year
df$year <- as.double(substr(df$date_month, 5, 9))


# Create dummy variables
df[List] <- lapply(df[List], function(x) as.integer(x > 0))
colnames(df)[colnames(df) %in% List] <- paste0(colnames(df)[colnames(df) %in% List], "_dummy")

# List variables
List <- grep("_dummy$", names(df), value = TRUE)

# Create lags
df <- Lag_12(df, iso3c, List)

# Clean names
df <- janitor::clean_names(df)

  
  return(df)
}

# Process each dataset
EM_dat_processed_2 <- process_EmDat_2(EM_dat, df_Base_YM)


```

#### Getting it in a country-year panel format
```{r}
process_EmDat_3 <- function(df, df_basey) {
  df <- df %>%
    group_by(iso3c, year) %>%
     dplyr::summarize(
      across(ends_with("_dummy"), sum)
    )
  
  # create dummy variables
  List <- setdiff(names(df), c("iso3c", "year"))
  for (variable in List) {
    new_name <- sub("_n_m$", "_dummy", variable)
    df[[new_name]] <- ifelse(df[[variable]] == 0, 0, 1)
  }
  
  # Merge with Base
  df <- left_join(df_basey, df, by = c("year", "iso3c"))
  
  # Assign 0s
  df <- df %>%
    mutate(across(List, ~ replace_na(., 0)))
  
  # Lag 12
  df <- Lag_12(df, iso3c, List)
  
  # Clean names
  df <-  janitor::clean_names(df)
  
  return(df)
}

# Process each dataset
EM_dat_processed_3 <- process_EmDat_3(EM_dat_processed_2, df_Base_Y)


```


# Merge datasets main independent and controls
```{r}
## add humanitarian dfs
df_main <- left_join(df_basey, EM_dat_processed_3, by = c("year" = "year", "iso3c" = "iso3c"))
## add vdem indexes
df_main <- left_join(df_main, df_precipitation, by = c("year" = "year", "iso3c" = "iso3c"))
## add conf events
df_main <- left_join(df_main, df_temperatures, by = c("year" = "year", "iso3c" = "iso3c"))
## add geo and colonial eritage
df_main <- left_join(df_Ind_var, df_rugged, by = c("iso3c" = "iso3c"))
```











