---
title: "analisi preliminare"
author: "MNB"
date: "4/25/2024"
output: html_document
---

## 28 1 2025
# Restart R
```{r}
#.rs.restartR()
```

# load libraries
```{r, include=FALSE}
library(plyr)
library(dplyr)
library(tidyverse)
library(tidyr)
library(naniar)
#library(ggplot2)
#library(stargazer)
#library(brms)
#library(sandwich)
library(lmtest)
library(magrittr) # for pipes
library(nnet) # for the multinom()-function
library(MASS) # for the multivariate normal distribution

# The package
library(MNLpred)

# Plotting the predicted probabilities:
library(scales)

```


# Remove lists 
```{r, include=FALSE}
## remove lists
rm(list=ls())
```

# Functions
```{r, include=FALSE}
# exclude
'%!in%' <- function(x,y)!('%in%'(x,y))

# Function to scale a variable to the 0-1 range
scale_0_1 <- function(x) {
  (x - min(x, na.rm = TRUE)) / (max(x, na.rm = TRUE) - min(x, na.rm = TRUE))
}


# Define the function to generate a variable chain suitable for a model
gen_formula <- function(dependent_var, var_list) {
  # Concatenate the variable names with " + " as separator
  var_chain <- paste(var_list, collapse = " + ")

  complete_formula <- as.formula(paste(dependent_var, var_chain, sep = " ~ "))

    
  # Return the concatenated variable chain
  return(complete_formula)
}


```


# Import DFs
## Set folders
```{r}
## set url Marco Nextclod
desktop_path <- file.path("C:", "Users", "marco", "Nextcloud")
#desktop_path <- file.path("C:", "Users", "krogers", "Nextcloud")

main_folder_name <- "Global Solidarity"
sub_folder_name <- "Compiled"



```

## Import Globsol dataset
### 50k 500d
```{r}
# # set DF
# DF<-c("globsol_df5k_500d.rds")
# # load DF
# Df_path <- file.path(desktop_path, main_folder_name, sub_folder_name, DF )
# # importing DF 
# df_Globsol5k500d <- readRDS(Df_path)

```




### 5k
```{r}
# set DF
DF<-c("globsol_df5k_v2.rds")
# load DF
Df_path <- file.path(desktop_path, main_folder_name, sub_folder_name, DF )
# importing DF
df_Globsol5k <- readRDS(Df_path)

```

### 50k
```{r}
# set DF
DF<-c("globsol_df50k_v2.rds")
# load DF
Df_path <- file.path(desktop_path, main_folder_name, sub_folder_name, DF )
# importing DF 
df_Globsol50k <- readRDS(Df_path)

```


### 100k
```{r}
# set DF
DF<-c("globsol_df100k_v2.rds")
# load DF
Df_path <- file.path(desktop_path, main_folder_name, sub_folder_name, DF )
# importing DF 
df_Globsol100k <- readRDS(Df_path)

```


## Import Independent and control variables
```{r}
# set DF
DF<-c("df_ind_var_v3.rds")
# load DF
Df_path <- file.path(desktop_path, main_folder_name, sub_folder_name, DF )
# importing DF 
df_IndVars <- readRDS(Df_path)

```

# Set dataset for analysis
```{r}
#df_DepVars <-df_Globsol5k
df_DepVars  <-df_Globsol50k
#df_DepVars <-df_Globsol100k
#df_DepVars <-df_Globsol5k500d

```

# Merge dfs
```{r}
df_full <- left_join(df_DepVars, df_IndVars, by = c("year" = "year", "iso3c" = "iso3c"))

## remove useless vars
# keep var of interest
df_full <- df_full[ , names(df_full) %!in% c("country.x",
                                            "country.y",
                                            "country_wb",
                                            "disaster")] 
```

# start analysis
## preprocess data
```{r}
## select vars if interest
List<-c("count_HO_lag_1",
        "nat_rents_lag_1",
        "trade_part_lag_1",
        "exp_part_lag_1",
        "impo_part_lag_1",
        "N_donors_lag_1",
        "pop_tot_lag_1",
        "gdp_lag_1",
        "gdp_per_cap_ppp_lag_1",
        "inflation_lag_1",
        "urb_pop_pct_lag_1",
        "trade_lag_1",
        "inf_mort_rate_lag_1",
        "liberal_demo_lag_1",
        "regime_corruption_lag_1",
        "civil_soc_lag_1",
        "best_fat_lag_1",
        "food_export_lag_1",
        "food_import_lag_1",
        "biological_dummy_50k",
        "biological_dummy_lag_1_50k",
        "climatological_dummy_50k",
        "climatological_dummy_lag_1_50k",
        "geophysical_dummy_50k",
        "geophysical_dummy_lag_1_50k",
        "hydrological_dummy_50k",
        "hydrological_dummy_lag_1_50k",
        "meteorological_dummy_50k",
        "meteorological_dummy_lag_1_50k",
        "colony_fra",
        "colony_gbr",
        "colony_oeu",
        "colony_prt",
        "colony_esp",
        "tropical",
        "desert",
        "N_memberships",
        "NS_donors_ratio_lag_1",
        "fuel_income_lag_1",
        "rpe_agri_lag_1",
        "rpe_gdp_lag_1",
        "rpe_gdp_nonres_lag_1",
        "military_exp_pct_gdp_lag_1",
        "military_exp_pct_gov_exp_lag_1",
        "KOFTrGI_lag_1",
        "KOFIpGI_lag_1",
        "KOFCuGI_lag_1",
        "KOFPoGI_lag_1",
        "gas_rents_lag_1",
        "oil_rents_lag_1",
        "minerals_rents_lag_1",
        "service_va_lag_1",
        "export_wb_lag_1",
        "import_wb_lag_1",
        "agricolture_va_lag_1",
        "rugged",
        "gdp_grwt_lag_1",
        "fdi_lag_1",
        "military_centr_lag_1",
        "mil_per_lag_1",
        "dis_death",
        "DamAd",
        "mil_exp_usd_lag_1",
        "autonomy_lag_1",
        "executive_corr_lag_1",
        "civil_soc_lag_1",
        "v2regdur",
        "age_dep_ratio_lag_1",
        "lit_rate_lag_1",
                   "regio_pol",
                   "regio_geo",
        "commitment_tot_lag_1",
                                                        "commitment_tot_pc_lag_1",
        "commitment_tot_lag_1",
                                                        "commitment_tot_pc_lag_1")

df_model_data <- df_full[ , names(df_full) %in% c(List,"GlobSol","Hum_plus_ER_aid_tot","NormAgr","iso3c","year")] 

## drop NAs
#df_model_data <- na.omit(df_model_data)

# List of variable names to scale
#variables_to_scale <- List

# List of variable names to scale
df_scaled<-df_model_data

# log variables
#df_scaled$ln_GDP_lag_1<-log(df_scaled$gdp_lag_1)
#df_scaled$ln_gdp_per_cap_ppp_lag_1<-log(df_scaled$gdp_per_cap_ppp_lag_1)
#df_scaled$ln_pop_tot_lag_1<-log(df_scaled$pop_tot_lag_1)
#df_scaled$ln_trade_lag_1<-log(df_scaled$trade_lag_1)
#df_scaled$ln_fuel_income_lag_1<-log((1+df_scaled$fuel_income_lag_1))

# #retain unscaled for model precision checks
# df_scaled$ln_GDP_lag_1_unscaled<-df_scaled$ln_GDP_lag_1
# df_scaled$ln_pop_tot_lag_1_unscaled<-df_scaled$ln_pop_tot_lag_1
# df_scaled$ln_trade_lag_1_unscaled<-df_scaled$ln_trade_lag_1
# df_scaled$ln_fuel_income_lag_1_unscaled<-df_scaled$ln_fuel_income_lag_1
# df_scaled$gdp_lag_1_unscaled<-df_scaled$gdp_lag_1
# df_scaled$pop_tot_lag_1_unscaled<-df_scaled$pop_tot_lag_1
# df_scaled$trade_lag_1_unscaled<-df_scaled$trade_lag_1
# df_scaled$fuel_income_lag_1_unscaled<-df_scaled$fuel_income_lag_1
# df_scaled$ln_gdp_per_cap_ppp_lag_1_unscaled<-df_scaled$ln_gdp_per_cap_ppp_lag_1
# df_scaled$gdp_per_cap_ppp_lag_1_unscaled<-df_scaled$gdp_per_cap_ppp_lag_1
# 
## scale varaibles
#df_scaled$nat_rents_lag_1<-(df_scaled$nat_rents_lag_1)/100
#df_scaled$urb_pop_pct_lag_1<-(df_scaled$urb_pop_pct_lag_1)/100
#df_scaled$tropical<-(df_scaled$tropical)/100
#df_scaled$desert<-(df_scaled$desert)/100
#df_scaled$gdp_per_cap_ppp_lag_1<-df_scaled$gdp_per_cap_ppp_lag_1/100

#variables_to_scale <- c("ln_GDP_lag_1","ln_pop_tot_lag_1","ln_trade_lag_1","ln_fuel_income_lag_1",
#                       "gdp_lag_1", "pop_tot_lag_1","trade_lag_1","fuel_income_lag_1",
#                       "ln_gdp_per_cap_ppp_lag_1","gdp_per_cap_ppp_lag_1")
#df_scaled[variables_to_scale] <- lapply(df_scaled[variables_to_scale], scale_0_1)

## set fixed effects
#df_scaled$iso3c <- as.factor(df_scaled$iso3c)
#df_scaled$year <- as.factor(df_scaled$year)

# Check the distribution of the Globsol variable
table(df_scaled$GlobSol)

#add index column to data frame
df_scaled$index <- 1:nrow(df_scaled)

##
df_scaled$colony<-ifelse(df_scaled$colony_fra==1|
                           df_scaled$colony_gbr==1|
                           df_scaled$colony_oeu==1 |
                           df_scaled$colony_prt==1 |
                           df_scaled$colony_esp==1,1,0)

## disaster count
df_scaled$dis_count<-df_scaled$biological_dummy_50k+df_scaled$climatological_dummy_50k+df_scaled$geophysical_dummy_50k+df_scaled$hydrological_dummy_50k+df_scaled$meteorological_dummy_50k
df_scaled$dis_count_lag_1<-df_scaled$biological_dummy_lag_1_50k+df_scaled$climatological_dummy_lag_1_50k+df_scaled$geophysical_dummy_lag_1_50k+df_scaled$hydrological_dummy_lag_1_50k+df_scaled$meteorological_dummy_lag_1_50k

## create variable last_time: last time a counry experienced th type of solidarity is experiencing now
df_scaled <- df_scaled %>%
  arrange(iso3c, year) %>%
  group_by(iso3c) %>%
  mutate(Last_time = {
    last_time <- rep(NA, n())  # Initialize result vector
    for (i in seq_len(n())) {
      current_globsol <- GlobSol[i]
      current_year <- year[i]
      past_rows <- which(GlobSol[1:(i - 1)] == current_globsol)  # Find past occurrences
      if (length(past_rows) > 0) {
        last_time[i] <- current_year - year[max(past_rows)]  # Years since last occurrence
      }
    }
    last_time
  }) %>%
  ungroup()

# Replace 0s with NA in variable X
df_scaled$Last_time[df_scaled$Last_time == 0] <- NA

```

## Export file
```{r}
#saving it
#namefile<-"df_full_v3_5000.csv"
namefile<-"df_full_v3.csv"
#namefile<-"df_full_v2_100000.csv"
#namefile<-"df_full_5k_500d.csv"

## correct names
df_scaled<-janitor::clean_names(df_scaled)

folder_path_wb <- file.path(desktop_path, main_folder_name, sub_folder_name, namefile)
write.csv(df_scaled, folder_path_wb, row.names = FALSE,na = "")  # row.names = FALSE to exclude row indices

```


## Set variables
```{r}
# # Define the dependent variable and set is as an unordered factors
# dependent_var <- "GlobSol"
# df_scaled$GlobSol <- factor(df_scaled$GlobSol)  # Ensure it's a factor
# # Re-level the target variable to set 4 as the baseline
# df_scaled$GlobSol <- relevel(df_scaled$GlobSol, ref = "4")
# 
# 
# main_indip <- c("trade_part_lag_1","gdp_per_cap_ppp_lag_1", "nat_rents_lag_1")
# 
# econ_deve <- c("trade_lag_1","ln_pop_tot_lag_1","urb_pop_pct_lag_1","inf_mort_rate_lag_1","inflation_lag_1")
# cof<- c("best_fat_lag_1")
# pol <- c("liberal_demo_lag_1","rpe_agri_lag_1")
# disaster <- c("dis_count")
# disaster_lagged <- c("dis_count_lag_1")
# 
# disaser_extended <- c("biological_dummy_50k",
#                     "climatological_dummy_50k",
#                     "geophysical_dummy_50k",
#                     "hydrological_dummy_50k",
#                     "meteorological_dummy_50k")
# 
# disaser_extended_lag <- c("biological_dummy_lag_1_50k",
#                     "climatological_dummy_lag_1_50k",
#                     "geophysical_dummy_lag_1_50k",
#                     "hydrological_dummy_lag_1_50k",
#                     "meteorological_dummy_lag_1_50k")
# 
# geo_colonial <-c("desert","colony")

```


## Run multinomial models
```{r}
# # Full controls
# Vars<-c(main_indip,econ_deve,cof,pol,geo_colonial,disaster)
# full_model_df<- df_scaled[complete.cases(df_scaled[, c(dependent_var,Vars)]), ]
# full_model_df <- full_model_df[, c("iso3c","year",dependent_var,Vars)]
# 
# # baseline model
# Vars<-c(main_indip)
# # Create the complete formula
# complete_formula <-gen_formula(dependent_var,Vars)
# # Estimate the multinomial logistic regression model
# multinom_model1 <- multinom(complete_formula, data = full_model_df)
# 
# # Development controls
# Vars<-c(main_indip,econ_deve)
# # Create the complete formula
# complete_formula <-gen_formula(dependent_var,Vars)
# # Estimate the multinomial logistic regression model
# multinom_model2 <- multinom(complete_formula, data = full_model_df)
# 
# # Full controls
# Vars<-c(main_indip,econ_deve,cof,pol,geo_colonial,disaster)
# # Create the complete formula
# complete_formula <-gen_formula(dependent_var,Vars) 
# # Estimate the multinomial logistic regression model
# multinom_model3 <- multinom(complete_formula, data = full_model_df)

```

```{r}

# summary(multinom_model1)
# length(multinom_model1$fitted.values)
# n_obs <- nrow(model.frame(multinom_model1))
# n_obs

```


```{r}
# stargazer(multinom_model1, 
#           type = "text",  # Output type: "text" for console or text file, "html" or "latex" for others
#           out = "test.txt",  # Specify the output file
#           title = "Multinomial Logistic Regression Results",  # Optional: add a title
#           digits = 2,  # Number of decimal places to display
#           omit.stat = c("aic", "bic"),  # Omit statistics like AIC, BIC if not needed
#           single.row = TRUE)  # Optional: format coefficients in a single row

```


## plot results tables
```{r}
# # Create a comparison table with stargazer
# stargazer(
#   multinom_model1, multinom_model2, 
#   multinom_model3,
#   type = "html",  # or "latex" or "html" for different output formats
#   title = "Comparison of Multinomial Models",
#   align = TRUE,
#   no.space = TRUE,
#   digits = 3,
#   out="table.html"
# )


```


## Model precision check
```{r}
#library(texreg)

# All unlogged GDPpc models outperform logged GDPpc models
# Unlog trade, log population outperforms log-log and unlog-unlog combinations
# Exclude corruption - similar to liberal_demo: Including only corruption slightly poorer fit than only liberal_demo, much poorer including both.
# Exclude disaster type - similar to disaster count: Including only type poorer fit than only count, much poorer including both.
# Exclude tropical - not significant, reduces model fit
# Add RPE (agri), infant mortality, inflation

#screenreg(list(multinom_model1,multinom_model2,multinom_model3))

```


## Export full model df
```{r}
# #saving it
# namefile<-"full_model_df.csv"
# folder_path_wb <- file.path(desktop_path, main_folder_name, sub_folder_name, namefile)
# write.csv(full_model_df, folder_path_wb, row.names = FALSE,na = "")  # row.names = FALSE to exclude row indices

```

### probabilities with marginal intervals
```{r}
# # Full controls
# Vars<-c(main_indip,econ_deve,cof,pol,geo_colonial,disaster)
# 
# # Create the complete formula
# complete_formula <-gen_formula(dependent_var,Vars) 
# # Estimate the multinomial logistic regression model
# mod1 <- multinom(complete_formula, data = full_model_df,
#                             Hess = TRUE)
# 
# gles<-full_model_df
# 
# 
# globsol_labels <- c("1" = "Cosmopolitan",
#                     "2" = "Commitment problem",
#                     "3" = "Post-colonial",
#                     "4" = "Communitarian")
# 
# globsol_colours <- c("1"="#E41A1C", "2"="#377EB8", "3"="#4DAF4A", "4"="#984EA3")
# 
# pred1 <- mnl_pred_ova(model = mod1,
#                       data = gles,
#                       x = "trade_part_lag_1",
#                       by = 1,
#                       seed = "random", # default
#                       nsim = 100, # faster
#                       probs = c(0.025, 0.975)) # default
# 
# min(full_model_df$trade_part_lag_1)
# max(full_model_df$trade_part_lag_1)
# 
# pred1$plotdata$GlobSolOrdered <- factor(pred1$plotdata$GlobSol, levels = c("3", "1", "4", "2"))
# 
# ggplot(data = pred1$plotdata, aes(x = trade_part_lag_1, 
#                                   y = mean,
#                                   ymin = lower, ymax = upper)) +
#   scale_fill_manual(values=globsol_colours,labels=globsol_labels, guide="none") +
#   scale_colour_manual(values=globsol_colours,labels=globsol_labels, guide="none") +
#   geom_ribbon(aes(fill = GlobSol), alpha = 0.2, colour = NA) +  # Confidence intervals with no border color
#   geom_line(aes(colour = GlobSol)) +  # Mean line with color
#    facet_wrap(~ GlobSolOrdered, scales = "fixed", ncol = 2, labeller = labeller(GlobSolOrdered = as_labeller(globsol_labels))) +
#   scale_y_continuous(labels = percent_format(accuracy = 1)) + # % labels
#   scale_x_continuous(breaks = seq(60,240,20)) +
#   theme_bw() +
#   # theme(
#   #   axis.text.x = element_text(angle = 45, hjust = 1),  # Tilt x-axis labels
#   #   axis.text.y = element_text(angle = 45, vjust = 1)   # Tilt y-axis labels (if needed)
#   # ) +
#   labs(y = "Predicted probabilities",
#        x = "Number of trade partners")  +
#   theme(strip.text = element_text(face = "bold"))
# 
# ggsave(paste0(userpath,"Nextcloud/Global Solidarity/Figures/trade_partners.png"))
# 
# min(full_model_df$gdp_per_cap_ppp_lag_1)
# max(full_model_df$gdp_per_cap_ppp_lag_1)
# 
# 
# pred1 <- mnl_pred_ova(model = mod1,
#                       data = gles,
#                       x = "gdp_per_cap_ppp_lag_1",
#                       by = 10,
#                       seed = "random", # default
#                       nsim = 100, # faster
#                       probs = c(0.025, 0.975)) # default
# 
# pred1$plotdata$GlobSolOrdered <- factor(pred1$plotdata$GlobSol, levels = c("3", "1", "4", "2"))
# 
# 
# ggplot(data = pred1$plotdata, aes(x = gdp_per_cap_ppp_lag_1, 
#                                   y = mean,
#                                   ymin = lower, ymax = upper)) +
#   scale_fill_manual(values=globsol_colours,labels=globsol_labels, guide="none") +
#   scale_colour_manual(values=globsol_colours,labels=globsol_labels, guide="none") +
#   geom_ribbon(aes(fill = GlobSol), alpha = 0.2, colour = NA) +  # Confidence intervals with no border color
#   geom_line(aes(colour = GlobSol)) +  # Mean line with color
#   facet_wrap(~ GlobSolOrdered, scales = "fixed", ncol = 2, labeller = labeller(GlobSolOrdered = as_labeller(globsol_labels))) +
#   scale_y_continuous(labels = percent_format(accuracy = 1)) + # % labels
#   scale_x_continuous(breaks = seq(0, 600, 50)) +
#   theme_bw() +
#   labs(y = "Predicted probabilities",
#        x = "GDP per capita ($US hundreds)") +
#   theme(strip.text = element_text(face = "bold"))
# 
# ggsave(paste0(userpath,"Nextcloud/Global Solidarity/Figures/GDPpc.png"))
# 
# 
# pred1 <- mnl_pred_ova(model = mod1,
#                       data = gles,
#                       x = "nat_rents_lag_1",
#                       by = 0.5,
#                       seed = "random", # default
#                       nsim = 100, # faster
#                       probs = c(0.025, 0.975)) # default
# 
# 
# pred1$plotdata$GlobSolOrdered <- factor(pred1$plotdata$GlobSol, levels = c("3", "1", "4", "2"))
# 
# ggplot(data = pred1$plotdata, aes(x = nat_rents_lag_1, 
#                                   y = mean,
#                                   ymin = lower, ymax = upper)) +
#   scale_fill_manual(values=globsol_colours,labels=globsol_labels, guide="none") +
#   scale_colour_manual(values=globsol_colours,labels=globsol_labels, guide="none") +
#   geom_ribbon(aes(fill = GlobSol), alpha = 0.2, colour = NA) +  # Confidence intervals with no border color
#   geom_line(aes(colour = GlobSol)) +  # Mean line with color
#   facet_wrap(~ GlobSolOrdered, scales = "fixed", ncol = 2, labeller = labeller(GlobSolOrdered = as_labeller(globsol_labels))) +
#   scale_y_continuous(labels = percent_format(accuracy = 1)) +  # % labels
#   scale_x_continuous(breaks = seq(0, 50, 5)) +
#   theme_bw() +
#   labs(y = "Predicted probabilities",
#        x = "Natural Resource Rents (% GDP)") +
#   theme(strip.text = element_text(face = "bold"))
# 
# ggsave(paste0(userpath,"Nextcloud/Global Solidarity/Figures/natural_resources.png"))




```

```{r}
# library(broom)
# library(marginaleffects)
# library(ggstance)
# 
# ame <- avg_slopes(mod1,variables = main_indip)
# 
# ame$term<-ifelse(ame$term=="gdp_per_cap_ppp_lag_1","GDP per capita ($US hundreds)",
#           ifelse(ame$term=="nat_rents_lag_1", " Natural resource rents (% GDP)",
#                  "Trade partners"))
# 
# 
# ggplot(ame, aes(x=estimate,y=term,colour=group))+ 
#   geom_vline(xintercept=0,linetype="dashed",color = "black", size=0.5)+
#   geom_pointrangeh(aes(xmin=conf.low,
#                      xmax=conf.high),
#     position=position_dodgev(height=0.75))+
#   ylab("Independent variables")+xlab("Average marginal effect")+
#    scale_colour_manual(values=globsol_colours,name="Global Solidarity pattern",
#                      labels=globsol_labels)+
# theme_minimal() + theme(panel.grid.major = element_blank(), panel.grid.minor= element_blank(),
#                         legend.title = element_text(size=10),
#                         axis.ticks.x = element_line(colour="black"))
# 
# ggsave(paste0(userpath,"Nextcloud/Global Solidarity/Figures/AME.png"))

```
#Check model representativeness
```{r}
# df<- readRDS(file.path(desktop_path, main_folder_name,sub_folder_name,"globsol_20240313_df50k.rds"))
# 
# full_model_df<- read_csv(file.path(desktop_path, main_folder_name,sub_folder_name,"full_model_df.csv"))
# 
# # check distribution of missing values
# check<-full_model_df %>% group_by(GlobSol) %>%
#   summarise(count=n())%>%
#   mutate(pc=count/sum(count))
# 
# tmp<-df %>% group_by(GlobSol) %>%
#   summarise(count_miss=n())%>%
#   mutate(pc_miss=count_miss/sum(count_miss))
# 
# check<-left_join(check,tmp)
```
