---
title: "main_independent_variables"
author: "MNB"
date: "4/18/2024"
output: html_document
---

## 09 12 2024
## Libraries
```{r, include=FALSE}
library(Hmisc)
library(data.table)

library(R.utils)
library(plyr)
library(dplyr)
library(tidyverse)
library(tidyr)
library(naniar)
library(geosphere)
library(zoo)
library(stringr)
library(tidytext)
#library(rworldmap)
library(gridExtra)


library(classInt)
#library("ggplot2")
library(devtools)
library(DT)
library(dvmisc)
library(ggpubr)
library(gtools)
library(foreign)

#library(spdep)
library(lubridate)


library(WDI)
library(readxl)
library(haven)


library(reshape)

library(geojsonio)

library(countrycode)

library(roll)
```

# Remove lists 
```{r, include=FALSE}
## remove lists
rm(list=ls())
```

# Funtions 
```{r, include=FALSE}

# exclude
'%!in%' <- function(x,y)!('%in%'(x,y))

drop_columns <- function(data, columns_to_drop) {
  data <- data[, names(data) %!in% columns_to_drop, drop = FALSE]
  return(data)
}


## drop NAs from column
Drop_NA <- function(dataset, col_name){
  col_name <- enquo(col_name)
  dataset %>%
    drop_na((!!col_name)) %>%
    as.data.frame()
}

## create 1 and 2 period lags (grouping by a variable)
Lag_12 <- function(dataset,col_name,x){
  {
    col_name <- enquo(col_name)
    dataset %>%
      group_by(!!col_name) %>%
      mutate(across(all_of(x),
                    .fns = ~ lag(.,1),
                    .names = paste0("{.col}_lag_",1)))%>%
      mutate(across(all_of(x),
                    .fns = ~ lag(.,2),
                    .names = paste0("{.col}_lag_",2)))
    
  } 
}

## create 1 and 2 period lags 
Lag_12_ngby <- function(dataset,x){
  {
    dataset %>%
      mutate(across(all_of(x),
                    .fns = ~ lag(.,1),
                    .names = paste0("{.col}_lag_",1)))%>%
      mutate(across(all_of(x),
                    .fns = ~ lag(.,2),
                    .names = paste0("{.col}_lag_",2)))
    
  } 
}

## assign 0 to NAs
Nas_to_0 <- function(dataset, x) {
  
  dataset %>% mutate_at(all_of(x), ~replace(., is.na(.), 0))
  
}


download_and_create_folder <- function(file_name, desktop_path, folder_name, url) {
  
  # Combine the desktop path with the folder name
  folder_path <- file.path(desktop_path,main_folder_name, folder_name)
  
  
  # Check if the folder exists
  if (!file.exists(folder_path)) {
    # If the folder doesn't exist, create it
    dir.create(folder_path)
    cat("Folder", folder_path, "created.\n")
  } else {
    # If the folder already exists, do nothing
    cat("Folder", folder_path, "already exists.\n")
  }
  
  # Specify the file path where you want to save the downloaded file
  file_path <- paste0(folder_path, "/", file_name)
  
  # Download the file
  download.file(url, file_path, mode = "wb")
}




download_create_folder_and_unzip <- function(desktop_path, folder_name, url) {
  
  # Combine the desktop path with the folder name
  folder_path <- file.path(desktop_path,main_folder_name, folder_name)
  
  
  # Check if the folder exists
  if (!file.exists(folder_path)) {
    # If the folder doesn't exist, create it
    dir.create(folder_path)
    cat("Folder", folder_path, "created.\n")
  } else {
    # If the folder already exists, do nothing
    cat("Folder", folder_path, "already exists.\n")
  }
  
  # Specify the file path where you want to save the downloaded file
  file_path <- folder_path
  
  # Download the file
  download.file(url, destfile = "temp.zip", mode = "wb")
  
  # Unzip the downloaded file
  unzip("temp.zip", exdir = file_path)
  
  # Delete the temporary zip file
  file.remove("temp.zip")
}


# Define a function to rename specified columns with a given suffix
rename_columns <- function(df, suffix, vars_to_change) {
  # Create new names for the specified variables by adding the suffix
  new_names <- setNames(paste0(vars_to_change, suffix), vars_to_change)
  
  # Rename the columns in the data frame
  names(df)[names(df) %in% names(new_names)] <- new_names[names(df)[names(df) %in% names(new_names)]]
  
  # Return the modified data frame
  return(df)
}
```



# Setting directory for datasets' folders
```{r}
desktop_path <- file.path("C:", "Users", "marco", "Desktop")
#desktop_path <- file.path("C:", "Users","krogers","Documents")
```


# Set main folder name
```{r}
# Define the name of the folder to check/create
main_folder_name <- "DFGlobalLab"
#main_folder_name <- "data"
```

# Creating folder for datasets
```{r}

# Combine the desktop path with the folder name
folder_path <- file.path(desktop_path, main_folder_name)

# Check if the folder exists
if (!file.exists(folder_path)) {
  # If the folder doesn't exist, create it
  dir.create(folder_path)
  cat("Folder", main_folder_name, "created on the desktop.\n")
} else {
  # If the folder already exists, do nothing
  cat("Folder", main_folder_name, "already exists on the desktop.\n")
}
```

# Importing and reshaping Dfs

## Polity 2
#### Set subfolder name
```{r}
sub_folder_name<-"polity2"
```

#### Create folder and download
```{r}
# download_and_create_folder("p5v2018.xls",
#                            desktop_path,
#                            sub_folder_name,
#                            "http://www.systemicpeace.org/inscr/p5v2018.xls")
```

#### Import
```{r}
file_path<-file.path(desktop_path,main_folder_name, sub_folder_name, "p5v2018.xls")
## import  dataset
Polity2<- read_excel(file_path)
```

# Create bases - at year and month levels
```{r}
df_Polity2<-Polity2

# Create base at year level
## subset years of interests
df_Polity2<-subset(df_Polity2, df_Polity2$year>1980 & Polity2$year<2020)

# Rename countries
  replacements <- c(
    "Czechoslovakia"    = "Czech Republic (the)",
    "Serbia Montenegro" = "Serbia",
    "Yugoslavia"        = "Serbia"
  )
  df_Polity2$country <- ifelse(df_Polity2$country %in% names(replacements), replacements[df_Polity2$country], df_Polity2$country)

## assign ISO3C
df_Polity2$iso3c <- countrycode(df_Polity2$country, "country.name", "iso3c")

## subset only columns of interest
df_Base_Y<-df_Polity2[c("country",
                        "iso3c",
                        "year")]

# Complete panel
df_Base_Y<-df_Base_Y %>%
  complete(iso3c,year=c(1981:2021)) %>%
  group_by(iso3c) %>% fill(country) %>%
  ungroup()

## drop iso3c NA
df_Base_Y<-Drop_NA(df_Base_Y, iso3c)

#drop duplicates (usual yuogoslavia and soviet union "problem" with name change to serbia and russia)
df_Base_Y<-df_Base_Y %>% 
                distinct(year, iso3c , .keep_all = TRUE)

## correct names
df_Base_Y<-janitor::clean_names(df_Base_Y)

# Create base at month level
## set list of countries
Countries<-as.data.frame(unique(df_Base_Y$country))
names(Countries)[1] <- "country"
Countries$Dummy<-1
## assign ISO3C
Countries$iso3c <- countrycode(Countries$country, "country.name", "iso3c")
## set list of months
Date<-as.data.frame(seq(as.Date("1980-1-1"), as.Date("2021-12-31"), by = "month"))
names(Date)[1] <- "Date.month"
Date$Dummy<-1
Date$Date.month<-as.yearmon(Date$Date.month)
## create base
df_Base_YM<-left_join(Countries,Date)
## drop dummy
List<-c("Dummy")
df_Base_YM<-drop_columns(df_Base_YM,List)
## create year variable
df_Base_YM$year <- as.integer(c((substr(( c(df_Base_YM$Date.month)), 5, 8))))

## correct names
df_Base_YM<-janitor::clean_names(df_Base_YM)

```



## WB dataset
### Set subfolder name
```{r}
sub_folder_name<-"WorldBank"
```

### Create folder
```{r}

# Combine the desktop path with the folder name
folder_path <- file.path(desktop_path, main_folder_name, sub_folder_name)

# Check if the folder exists
if (!file.exists(folder_path)) {
  # If the folder doesn't exist, create it
  dir.create(folder_path)
  cat("Folder", main_folder_name, "created on the desktop.\n")
} else {
  # If the folder already exists, do nothing
  cat("Folder", main_folder_name, "already exists on the desktop.\n")
}
```

### WB: importing dataset via API
```{r}
# 
# WorldBank <- WDI(
#   country = "all",
#   indicator = c("Nat_rents"="NY.GDP.TOTL.RT.ZS",
#                 "oil_rents"="NY.GDP.PETR.RT.ZS",
#                 "gas_rents"="NY.GDP.NGAS.RT.ZS",
#                 "minerals_rents"="NY.GDP.MINR.RT.ZS",
#                 "GDP"="NY.GDP.MKTP.CD",
#                 "GDP_pc"="NY.GDP.PCAP.CD",
#                 "GDP_per_cap_PPP"="NY.GDP.PCAP.PP.KD",
#                 "GDP_grwt"="NY.GDP.MKTP.KD.ZG",
#                 "Inflation"="FP.CPI.TOTL.ZG",
#                 "Service_VA"="NV.SRV.TOTL.ZS",
#                 "Manuf_VA"="NV.IND.MANF.ZS",
#                 "Industry_VA"="NV.IND.TOTL.ZS",
#                 "Agricolture_VA"="NV.AGR.TOTL.ZS",
#                 "Pop_tot"="SP.POP.TOTL",
#                 "Age_dep_ratio"="SP.POP.DPND",
#                 "Inf_mort_rate"="SP.DYN.IMRT.IN",
#                 "Military_exp_pct_GDP"="MS.MIL.XPND.GD.ZS",
#                 "Military_exp_pct_Gov_exp"="MS.MIL.XPND.ZS",
#                 "Trade"="NE.TRD.GNFS.ZS",
#                 "Export_wb"="NE.EXP.GNFS.ZS",
#                 "Import_wb"="NE.IMP.GNFS.ZS",
#                 "FDI"="BX.KLT.DINV.WD.GD.ZS",
#                 "Mil_per"="MS.MIL.TOTL.P1",
#                 "Urb_pop_pct"="SP.URB.TOTL.IN.ZS",
#                 "Mil_exp_USD"="MS.MIL.XPND.CD",
#                 "lit_rate"="SE.ADT.1524.LT.ZS"
#   ),
#   start = 1980,
#   end = 2020,
#   extra = TRUE,
#   cache = NULL,
#   latest = NULL,
#   language = "en"
# )

```

### Setting path to save DF
```{r}
# setting path to save and import df
namefile<-"WorldBank.rds"
folder_path_wb <- file.path(desktop_path, main_folder_name, sub_folder_name, namefile)
```

### Saving DF
```{r}
#saving it

#saveRDS(WorldBank, folder_path_wb)

```

### Importing DF from folder
```{r}
#importing wb df
df_WorldBank <- readRDS(folder_path_wb)

## assign ISO3
names(df_WorldBank)[names(df_WorldBank) == "country"] <- "country_wb"
df_WorldBank$iso3c <- countrycode(df_WorldBank$country_wb, "country.name", "iso3c")

#drop iso3c NAs
df_WorldBank<-Drop_NA(df_WorldBank, iso3c)

#sort dataframe
df_WorldBank<-df_WorldBank[
  with(df_WorldBank, order(iso3c, year)),
]


## clean 
df_WorldBank <- df_WorldBank[ , ! names(df_WorldBank) %in% c("capital",
                                                             "longitude",
                                                             "latitude",
                                                             "income", 
                                                             "lending",
                                                             "iso2c",
                                                             "country_wb",
                                                             "country")]


# left join with base year
df_WorldBank <- left_join(df_Base_Y, df_WorldBank, by = c("year" = "year", "iso3c" = "iso3c"))
df_WorldBank <- dplyr::select(df_WorldBank, -country)


#list variables aiddata sectoral
List<- colnames(df_WorldBank)[!colnames(df_WorldBank) %in% c("iso3c",
                                                             "year",
                                                             "region")]

## lag variables of 1 to 2 years
df_WorldBank<-Lag_12(df_WorldBank, iso3c, List)

#correct names
df_WorldBank<-janitor::clean_names(df_WorldBank)

```
# NMC (add dataset)
```{r}

```


## V-Dem dataset for additioal polity controls
### Set subfolder name
```{r}
sub_folder_name<-"Vdem"
```

### Create folder
```{r}

# Combine the desktop path with the folder name
folder_path <- file.path(desktop_path, main_folder_name, sub_folder_name)

# Check if the folder exists
if (!file.exists(folder_path)) {
  # If the folder doesn't exist, create it
  dir.create(folder_path)
  cat("Folder", main_folder_name, "created on the desktop.\n")
} else {
  # If the folder already exists, do nothing
  cat("Folder", main_folder_name, "already exists on the desktop.\n")
}
```
### Add to the folder the videm dataset manually
### Import dataset
```{r}
namefile<-c("V-Dem-CY-Full+Others-v14.rds")
folder_path <- file.path(desktop_path, main_folder_name, sub_folder_name, namefile)

#import df_Vdem
Vdem<- readRDS(folder_path)
df_Vdem<-Vdem


```

### Subset variables of interest
```{r}


#subset years
df_Vdem<-subset(df_Vdem, df_Vdem$year>=1980)

#rename columns
names(df_Vdem)[names(df_Vdem) == "country_text_id"] <- "iso3c"
names(df_Vdem)[names(df_Vdem) == "country_name"] <- "country_Vdem"

#subset variables of interests
df_Vdem_s<-df_Vdem[c("iso3c",
                   "year",
                   "v2clstown",
                   "v2xnp_regcorr",
                   "v2x_regime_amb",
                   "v2cacamps",
                   "e_gdp",
                   "e_gdppc",
                   "e_polity2",
                   "v2x_ex_military",
                   "v2dlencmps",
                   "v2svdomaut",
                   "e_regionpol_6C",
                   "v2xcs_ccsi",
                   "v2xnp_client",
                   "v2x_pubcorr",
                   "v2excrptps",
                   "v2exthftps",
                   "v2svstterr",
                   "v2stfisccap",
                   "v2stcritapparm",
                   "v2x_corr",
                   "v2x_execorr",
                   "e_total_fuel_income_pc",
                   "v2x_polyarchy",
                   "v2x_libdem",
                   "v2x_partipdem",
                   "v2x_delibdem",
                   "v2x_egaldem",
                   "v3ststeecap",
                   "v2regdur",
                   "e_regionpol",
                   "e_regiongeo")]


#rename columns
names(df_Vdem_s)[names(df_Vdem_s) == "e_total_fuel_income_pc"] <- "fuel_income"
names(df_Vdem_s)[names(df_Vdem_s) == "v2x_polyarchy"]          <- "electoral_demo"
names(df_Vdem_s)[names(df_Vdem_s) == "v2x_libdem"]             <- "liberal_demo"
names(df_Vdem_s)[names(df_Vdem_s) == "v2x_partipdem"]          <- "part_demo"
names(df_Vdem_s)[names(df_Vdem_s) == "v2x_delibdem"]           <- "delib_demo"
names(df_Vdem_s)[names(df_Vdem_s) == "v2x_egaldem"]            <- "egal_demo"

names(df_Vdem_s)[names(df_Vdem_s) == "v2clstown"]              <- "state_ownership"
names(df_Vdem_s)[names(df_Vdem_s) == "v2xnp_regcorr"]          <- "regime_corruption"
names(df_Vdem_s)[names(df_Vdem_s) == "v2x_corr"]               <- "political_corr"
names(df_Vdem_s)[names(df_Vdem_s) == "v2x_execorr"]            <- "executive_corr"

names(df_Vdem_s)[names(df_Vdem_s) == "v2x_regime_amb"]         <- "regime_type"
names(df_Vdem_s)[names(df_Vdem_s) == "v2cacamps"]              <- "political_polarization"
names(df_Vdem_s)[names(df_Vdem_s) == "e_gdp"]                  <- "gdp_vdem"
names(df_Vdem_s)[names(df_Vdem_s) == "e_gdppc"]                <- "gdp_pc_vdem"
names(df_Vdem_s)[names(df_Vdem_s) == "e_polity2"]              <- "polity2"
names(df_Vdem_s)[names(df_Vdem_s) == "v2x_ex_military"]        <- "military_centr"
names(df_Vdem_s)[names(df_Vdem_s) == "v2dlencmps"]             <- "spending"
names(df_Vdem_s)[names(df_Vdem_s) == "v2svdomaut"]             <- "autonomy"
names(df_Vdem_s)[names(df_Vdem_s) == "e_regionpol_6C"]         <- "region_pg"
names(df_Vdem_s)[names(df_Vdem_s) == "v2xcs_ccsi"]             <- "civil_soc"

# names(df_Vdem_s)[names(df_Vdem_s) == "v2xnp_client"]           <- "clientelism_index"
# names(df_Vdem_s)[names(df_Vdem_s) == "v2x_pubcorr"]            <- "pub_sect_corr_index"
# names(df_Vdem_s)[names(df_Vdem_s) == "v2excrptps"]             <- "pub_sect_corr_exch"
# names(df_Vdem_s)[names(df_Vdem_s) == "v2exthftps"]             <- "pub_sect_theft"
# names(df_Vdem_s)[names(df_Vdem_s) == "v2svstterr"]             <- "state_auth_terr"
# names(df_Vdem_s)[names(df_Vdem_s) == "v2stfisccap"]            <- "revenues_source"
# names(df_Vdem_s)[names(df_Vdem_s) == "v2stcritapparm"]         <- "appointment_in_ssfs"

names(df_Vdem_s)[names(df_Vdem_s) == "e_regionpol"]            <- "regio_pol"
names(df_Vdem_s)[names(df_Vdem_s) == "e_regiongeo"]            <- "regio_geo"


# left join with base year
df_Vdem_s <- left_join(df_Base_Y, df_Vdem_s, by = c("year" = "year", "iso3c" = "iso3c"))
df_Vdem_s <- dplyr::select(df_Vdem_s, -country)



#list variables aiddata sectoral
List<- colnames(df_Vdem_s)[!colnames(df_Vdem_s) %in% c("iso3c",
                                                       "year",
                                                       "region")]

                           ## lag variables of 1 to 2 years
df_Vdem_s<-Lag_12(df_Vdem_s, iso3c, List)

#correct names
df_Vdem_s<-janitor::clean_names(df_Vdem_s)

```

## Number of IGOs a country is member of
## https://correlatesofwar.org/data-sets/IGOs/
### Set name folder
```{r}
sub_folder_name<-"IGOs"
```
### Create folder and download
```{r}
 download_create_folder_and_unzip(desktop_path,
                           sub_folder_name,
                            "https://correlatesofwar.org/wp-content/uploads/state_year_formatv3.zip")
```

### Import
```{r}
file_path<-file.path(desktop_path,main_folder_name, sub_folder_name, "state_year_formatv3.csv")
## import  dataset
df_IGOs<- read.csv(file_path)
```

### Organize data
```{r}
## subset years greater than 1989
df_IGOs<-subset(df_IGOs, df_IGOs$year>1988)
## assign iso3ccode
df_IGOs$iso3c <- countrycode(df_IGOs$ccode, "cown", "iso3c")

## count 1 and 2 across columns
### create list of vars to count
List<- colnames(df_IGOs)[colnames(df_IGOs) %!in% c("iso3c", "year", "ccode", "country","state")]
### count memberships
df_IGOs <- df_IGOs %>%
  rowwise() %>%
  mutate(
    N_memberships = sum(c_across(all_of(List)) %in% c(1, 2))
  ) %>%
  ungroup()

# keep vars of interest
df_IGOs <- df_IGOs[c("iso3c",
                     "year",
                     "N_memberships")]

# left join with base year
df_IGOs <- left_join(df_Base_Y, df_IGOs, by = c("year" = "year", "iso3c" = "iso3c"))
df_IGOs <- dplyr::select(df_IGOs, -country)



# create lags
List<-c("N_memberships")
df_IGOs <- Lag_12(df_IGOs, iso3c, List)
```


## Humanitarian organizations
## https://dataverse.harvard.edu/dataverse/isq
### Import dataset form folder 
```{r}
HOD_Dec_2021 <- read_dta("HOD_Dec_2021.dta")
```

### reshape dataset
```{r}
df_HOD_Dec_2021<-HOD_Dec_2021
## assign iso3c
df_HOD_Dec_2021$iso3c <- countrycode(df_HOD_Dec_2021$COUNTHQ, "cown", "iso3c")
## drop if iso3c is NA
df_HOD_Dec_2021<-Drop_NA(df_HOD_Dec_2021, iso3c)
##assign country name
df_HOD_Dec_2021$c_name<- countrycode(df_HOD_Dec_2021$COUNTHQ, "cown", "country.name")


# keep vars of interest
df_HOD_Dec_2021 <- df_HOD_Dec_2021[c("COUNTHQ",
                                       "iso3c",
                                       "c_name",
                                       "name",
                                       "year")]

# reshape to country panel
## create fake end date to 2021
df_HOD_Dec_2021$end_date<-2021
## drop if year is NA
df_HOD_Dec_2021<-Drop_NA(df_HOD_Dec_2021, year)

## Create date variables
df_HOD_Dec_2021$Date.start <- as.Date(paste0(df_HOD_Dec_2021$year,     "-", "01", "-01"))
df_HOD_Dec_2021$Date.end   <- as.Date(paste0(df_HOD_Dec_2021$end_date, "-", "01", "-01"))


## reshape
# Reshape dataset
df_HOD_Dec_2021_long <- df_HOD_Dec_2021 %>%
  group_by(iso3c, name) %>%
  summarise(date = list(seq(floor_date(min(Date.start), unit = "year"),
                            floor_date(max(Date.end), unit = "year"),
                            by = "year"))) %>%
  unnest(cols = c(date))

# Create variable year
df_HOD_Dec_2021_long$year <- as.double(substr(df_HOD_Dec_2021_long$date, 1, 4))

# collapse to country year and count number of organizations per country
## create dummy for count
df_HOD_Dec_2021_long$count <- 1
## collapse dataset
df_HOD_cy <- df_HOD_Dec_2021_long %>%
  group_by(iso3c, year) %>%
  summarise(count_HO = sum(count))

# left join with base year
df_HOD_cy <- left_join(df_Base_Y, df_HOD_cy, by = c("year" = "year", "iso3c" = "iso3c"))
df_HOD_cy <- dplyr::select(df_HOD_cy, -country)

# assign 0s to NAs
List<-c("count_HO")
df_HOD_cy<-Nas_to_0(df_HOD_cy,List)

# create lags
df_HOD_cy <- Lag_12(df_HOD_cy, iso3c, List)


## subset years of interest
df_HOD_cy<-subset(df_HOD_cy, df_HOD_cy$year>1980)


```

## Conflict activity (UCDP GED)
### Link df: https://ucdp.uu.se/downloads/index.html#ged_global
### Set subfldder name
```{r}
sub_folder_name<-"UCDP"
```

### Create folder and download
```{r}
# download_create_folder_and_unzip(desktop_path,
#                            sub_folder_name,
#                            "https://ucdp.uu.se/downloads/ged/ged231-csv.zip")
```

### Import
```{r}
file_path<-file.path(desktop_path,main_folder_name, sub_folder_name, "GEDEvent_v23_1.csv")
#file_path<-file.path("~/Documents/data/UCDP/GEDEvent_v23_1.csv")
## import  dataset
UCDP_GED<- read.csv(file_path)
```


### Reshaping UCDP GED
### Adjusting names of countries, setting variables etc.
```{r}
df_UCDP_GED<-UCDP_GED

#assign ISO3
df_UCDP_GED$iso3c <- countrycode(df_UCDP_GED$country, "country.name", "iso3c",
                                 custom_match = c("Yemen (North Yemen)" = "YEM"))

#create year month date
            df_UCDP_GED$month <- c((substr(( c(df_UCDP_GED$date_start)), 6, 7)))
            df_UCDP_GED$day<- c((substr(( c(df_UCDP_GED$date_start)), 9, 10)))

            df_UCDP_GED$day.month.year <- as.character(paste0(df_UCDP_GED$month,
                                                          "/",
                                                          df_UCDP_GED$day,
                                                          "/",
                                                          df_UCDP_GED$year))

            df_UCDP_GED$month.year <- as.character(paste0(df_UCDP_GED$year,
                                                      "-",
                                                      df_UCDP_GED$month))

            df_UCDP_GED$Date<-as.Date(df_UCDP_GED$day.month.year, format = "%m/%d/%Y")
            df_UCDP_GED$date_month<-as.yearmon(df_UCDP_GED$month.year)
```

### Getting it in a country-year panel format
```{r}

df_UCDP_GED_s<-df_UCDP_GED[c("iso3c",
                   "year",
                   "type_of_violence",
                   "best")]


## aggregate at country iso3c level
df_UCDP_GED_Y <- df_UCDP_GED_s %>%
  group_by(iso3c, year, type_of_violence) %>%
   dplyr::summarize(n_fatalities = sum(best, na.rm = TRUE))

#reshape
df_UCDP_GED_Y<-reshape2::dcast(df_UCDP_GED_Y, year+iso3c~`type_of_violence`)

## merge with Base
df_UCDP_GED_Y= left_join(df_Base_Y, df_UCDP_GED_Y, by = c("year" = "year", "iso3c" = "iso3c"))
df_UCDP_GED_Y <- dplyr::select(df_UCDP_GED_Y, -country)

## keep only years after 1990
df_UCDP_GED_Y<-subset(df_UCDP_GED_Y,df_UCDP_GED_Y$year>=1990)

#list variables ged
List<- colnames(df_UCDP_GED_Y)[colnames(df_UCDP_GED_Y) %!in% c("iso3c", "year")]

# assign 0s
df_UCDP_GED_Y<-Nas_to_0(df_UCDP_GED_Y,List)

#rename variables
names(df_UCDP_GED_Y)[names(df_UCDP_GED_Y) == "1"] <- "StateBased_conf_fat"
names(df_UCDP_GED_Y)[names(df_UCDP_GED_Y) == "2"] <- "NonState_conf_fat"
names(df_UCDP_GED_Y)[names(df_UCDP_GED_Y) == "3"] <- "OneSided_fat"


## full fatalities
df_UCDP_GED_Y$best_fat<-df_UCDP_GED_Y$StateBased_conf_fat+df_UCDP_GED_Y$NonState_conf_fat+df_UCDP_GED_Y$OneSided_fat


#list variables ged
List<- colnames(df_UCDP_GED_Y)[colnames(df_UCDP_GED_Y) %!in% c("iso3c", "year")]

## create lags
df_UCDP_GED_Y<-Lag_12(df_UCDP_GED_Y, iso3c, List)

```

## Trade partners
### Set subfolder name
```{r}
sub_folder_name<-"UN Comtrade"
```

### Create folder
```{r}

# Combine the desktop path with the folder name
folder_path <- file.path(desktop_path, main_folder_name, sub_folder_name)

# Check if the folder exists
if (!file.exists(folder_path)) {
  # If the folder doesn't exist, create it
  dir.create(folder_path)
  cat("Folder", main_folder_name, "created on the desktop.\n")
} else {
  # If the folder already exists, do nothing
  cat("Folder", main_folder_name, "already exists on the desktop.\n")
}
```
### manually add to the folder the single csv files from the cloud
### set path
```{r}
## set path
#file_path<-file.path(desktop_path,main_folder_name, sub_folder_name, "TradeData_")

#file_path <-"C:/Users/krogers/Nextcloud/Global Solidarity/UNcomtrade/UN Comtrade/TradeData_"

```

### import and compose dataset
```{r}
# #import datasets
# ldf <- list() # creates a list
# 
# for (k in 1994:2021){
# 
#  year<-paste0("",k,"")
#  File<-paste0(file_path,year,".csv")
#  df<- read.csv(File, header = TRUE, quote = "")
#  ldf[[k]]<-df
# 
# }
# 
# #bind datasets
# df_UNcomtrade <- do.call(rbind, ldf)
# # drop list
# rm(ldf)

```

### set folder path
```{r}
namefile<-"df_UNcomtrade.rds"
folder_path_UNcom <- file.path(desktop_path,main_folder_name, sub_folder_name, namefile)

#folder_path_UNcom <-"C:/Users/krogers/Nextcloud/Global Solidarity/UNcomtrade/df_UNcomtrade.rds"

```

### saving DF
```{r}
#saveRDS(df_UNcomtrade, folder_path_UNcom)

```

### import from main folder
```{r}
#importing wb df
#df_UNcomtrade <- readRDS(folder_path_UNcom)

```

### Count number of export partners for each country
```{r}
# ## subset export partners
# df_UNcomtrade_export<-subset(df_UNcomtrade, df_UNcomtrade$FlowCode=="X")
# 
# # collapse dataset
# df_UNcomtrade_export <- df_UNcomtrade_export %>%
#     group_by(ReporterISO, RefYear) %>%
#     summarise(exp_part = n_distinct(PartnerCode))
# 
# # left join with base year
# df_UNcomtrade_export <- left_join(df_Base_Y, df_UNcomtrade_export, by = c("year" = "RefYear", "iso3c" = "ReporterISO"))
# df_UNcomtrade_export <- dplyr::select(df_UNcomtrade_export, -country)
# 
# ## subset years for which we have data
# df_UNcomtrade_export<-subset(df_UNcomtrade_export, df_UNcomtrade_export$year>1993)


```

### Count number of import partners for each country
```{r}
# ## subset export partners
# df_UNcomtrade_import<-subset(df_UNcomtrade, df_UNcomtrade$FlowCode=="M")
# 
# # collapse dataset
# df_UNcomtrade_import <- df_UNcomtrade_import %>%
#     group_by(ReporterISO, RefYear) %>%
#     summarise(impo_part = n_distinct(PartnerCode))
# 
# # left join with base year
# df_UNcomtrade_import <- left_join(df_Base_Y, df_UNcomtrade_import, by = c("year" = "RefYear", "iso3c" = "ReporterISO"))
# df_UNcomtrade_import <- dplyr::select(df_UNcomtrade_import, -country)
# 
# ## subset years for which we have data
# df_UNcomtrade_import<-subset(df_UNcomtrade_import, df_UNcomtrade_import$year>1993)

```

### Count number of trade partners for each country
```{r}

# # collapse dataset
# df_UNcomtrade_imp_exp <- df_UNcomtrade %>%
#     group_by(ReporterISO, RefYear) %>%
#     summarise(trade_part = n_distinct(PartnerCode))
# 
# # left join with base year
# df_UNcomtrade_imp_exp <- left_join(df_Base_Y, df_UNcomtrade_imp_exp, by = c("year" = "RefYear", "iso3c" = "ReporterISO"))
# df_UNcomtrade_imp_exp <- dplyr::select(df_UNcomtrade_imp_exp, -country)
# 
# ## subset years for which we have data
# df_UNcomtrade_imp_exp<-subset(df_UNcomtrade_imp_exp, df_UNcomtrade_imp_exp$year>1993)

```

### Combine export and import
```{r}
# # left join dfs
# df_UNcomtrade_main <- left_join(df_UNcomtrade_export, df_UNcomtrade_import, by = c("year" = "year", "iso3c" = "iso3c"))
# df_UNcomtrade_main <- left_join(df_UNcomtrade_main, df_UNcomtrade_imp_exp, by = c("year" = "year", "iso3c" = "iso3c"))
# 
# #list variables aiddata sectoral
# List<- colnames(df_UNcomtrade_main)[!colnames(df_UNcomtrade_main) %in% c("iso3c",
#                                                              "year")]
# 
# ## lag variables of 1 to 2 years
# df_UNcomtrade_main<-Lag_12(df_UNcomtrade_main, iso3c, List)

```

## (AidData) count number of donors per each country
### Link df: https://www.aiddata.org/data/aiddata-core-research-release-level-1-v3-0
### Set name folder
```{r}
sub_folder_name<-"Aidata"
```
### Create folder and download
```{r}
# download_create_folder_and_unzip(desktop_path,
#                            sub_folder_name,
#                            "https://github.com/AidData-WM/public_datasets/releases/download/v3.0/AidDataCore_ResearchRelease_Level1_v3.0.zip")
```

### Import
```{r}
file_path<-file.path(desktop_path,main_folder_name, sub_folder_name, "AidDataCoreDonorRecipientYearPurpose_ResearchRelease_Level1_v3.0.csv")
## import  dataset
Aiddata<- read.csv(file_path)

```

### prepare dataset
```{r}
df_Aiddata<-Aiddata

#change names
df_Aiddata$recipient[df_Aiddata$recipient=="Yugoslavia"]            <- "Serbia"
df_Aiddata$recipient[df_Aiddata$recipient=="Serbia and Montenegro"] <- "Serbia"
df_Aiddata$recipient[df_Aiddata$recipient=="Soviet Union"]          <- "Russia"

#assign ISO3
df_Aiddata$iso3c <- countrycode(df_Aiddata$recipient, "country.name", "iso3c")

#drop iso3c NAs
df_Aiddata<-df_Aiddata[!is.na(df_Aiddata$iso3c), ]

#assign ISO3 donor
df_Aiddata$iso3c_donor <- countrycode(df_Aiddata$donor, "country.name", "iso3c")

```


### count number of donors per country
```{r}

#drop iso3c NAs
df_donors_state<-df_Aiddata[!is.na(df_Aiddata$iso3c_donor), ]
df_donors_nonstate<-df_Aiddata[is.na(df_Aiddata$iso3c_donor), ]



  df_donors_state<- df_donors_state %>% 
    group_by(iso3c, year) %>%
     dplyr::summarize(N_donors_state = n_distinct(donor))



  df_donors_nonstate<- df_donors_nonstate %>% 
    group_by(iso3c, year) %>%
     dplyr::summarize(N_donors_nonstate = n_distinct(donor))

  ## merge with base
df_donors_state <- left_join(df_Base_Y, df_donors_state, by = c("year" = "year", "iso3c" = "iso3c"))
df_donors_state <- dplyr::select(df_donors_state, -country)

df_donors_nonstate <- left_join(df_Base_Y, df_donors_nonstate, by = c("year" = "year", "iso3c" = "iso3c"))
df_donors_nonstate <- dplyr::select(df_donors_nonstate, -country)
  


#list variables
List<- c("N_donors_state")
# assign 0s
df_donors_state<-Nas_to_0(df_donors_state,List)
## assign NAs to post 2014
df_donors_state<-df_donors_state %>% mutate(across(List, ~replace(., year > 2013, NA)))


#list variables
List<- c("N_donors_nonstate")
# assign 0s
df_donors_nonstate<-Nas_to_0(df_donors_nonstate,List)
## assign NAs to post 2014
df_donors_nonstate<-df_donors_nonstate %>% mutate(across(List, ~replace(., year > 2013, NA)))


df_donors<- left_join(df_donors_state, df_donors_nonstate, by = c("year" = "year", "iso3c" = "iso3c"))

df_donors$NS_donors_ratio<-df_donors$N_donors_nonstate/(df_donors$N_donors_state+df_donors$N_donors_nonstate)

#list variables aiddata 
List<- c("N_donors_state","N_donors_nonstate","NS_donors_ratio")

## lag variables of 1 to 2 years
df_donors<-Lag_12(df_donors, iso3c, List)
```
## Diego Puga colonial heritage
## https://diegopuga.org/data/rugged/
### Set name folder
```{r}
sub_folder_name<-"Roughness"
```
### download dataset
```{r}

 # download_create_folder_and_unzip(desktop_path,
 #                            sub_folder_name,
 #                           "https://diegopuga.org/data/rugged/rugged_data.zip")

```

### Import
```{r}
file_path<-file.path(desktop_path,main_folder_name, sub_folder_name, "rugged_data.csv")
## import  dataset
df_rugged<- read.csv(file_path)
```

### process
```{r}
#change names
df_rugged$country[df_rugged$country=="Yugoslavia"]            <- "Serbia"
df_rugged$country[df_rugged$country=="Serbia and Montenegro"] <- "Serbia"

#assign ISO3
df_rugged$iso3c <- countrycode(df_rugged$country, "country.name", "iso3c")

#drop iso3c NAs
df_rugged<-df_rugged[!is.na(df_rugged$iso3c), ]
```

# KOF index
#### Set subfolder name
```{r}
sub_folder_name<-"KOF"
```

#### Create folder and download
```{r}
# download_and_create_folder("KOFGI_2023_public.xlsx",
#                            desktop_path,
#                            sub_folder_name,
#                            "https://ethz.ch/content/dam/ethz/special-interest/dual/kof-dam/documents/Globalization/2023/KOFGI_2023_public.xlsx")
```

#### Import
```{r}
file_path<-file.path(desktop_path,main_folder_name, sub_folder_name, "KOFGI_2023_public.xlsx")
## import  dataset
df_KOFIndex<- read_excel(file_path)

```

### process
```{r}

#assign ISO3
df_KOFIndex$iso3c <- countrycode(df_KOFIndex$country, "country.name", "iso3c")

#drop iso3c NAs
df_KOFIndex<-df_KOFIndex[!is.na(df_KOFIndex$iso3c), ]

# Select variables of interest
df_KOFIndex <- df_KOFIndex %>% dplyr::select(-country)

List=c("KOFCuGI",
       "KOFEcGI",
       "KOFFiGI",
       "KOFGI",
       "KOFGIdf",
       "KOFGIdj",
       "KOFInGI",
       "KOFIpGI",
       "KOFPoGI",
       "KOFSoGI",
       "KOFTrGI")

df_KOFIndex <- Lag_12(df_KOFIndex, iso3c, List)

```

# Relative Capacity
```{r}
library(readxl)

#userpath<-("C:/Users/krogers/")
#df_rpc<-read_excel(paste0(userpath,"Nextcloud/Global Solidarity/arpc_2020.xlsx"))

df_rpc <- read_excel("C:/Users/marco/Desktop/DFGlobalLab/RPE/arpc_2020.xlsx")

List=c("rpe_agri","rpe_gdp","rpe_gdp_nonres")

df_rpc <- Lag_12(df_rpc, ISO3, List)


```


## EMDAT data on disasters in the country
#### Set subfolder name
```{r}
sub_folder_name<-"EMDAT"
```

#### Importing dataset
```{r}
file_path<-file.path(desktop_path,main_folder_name, sub_folder_name, "emdat.dta")
## import  dataset
EMDAT<- haven::read_dta(file_path)
```


```{r}

# Function to process dataset
process_EmDat_1 <- function(data, min_affected) {
  # Subset years
  data <- subset(data, StartYear >= 1980)
  
  # Subset only big disasters
  data <- subset(data, NoAffected > min_affected)
  
  # Drop technological disasters
  data <- subset(data, DisasterGroup == "Natural")
  
  # Select variables of interest
  data <- data[c("DisNo",
                 "StartYear",
                 "EndYear",
                 "StartMonth",
                 "EndMonth",
                 "DisasterGroup",
                 "DisasterSubgroup",
                 "DisasterType",
                 "DisasterSubtype",
                 "ISO",
                 "Country")]
  
  # Rename variables
  names(data)[names(data) == "Year"]    <- "year"
  names(data)[names(data) == "Country"] <- "country_Emdat"
  
  # Drop events without date
  data <- data[complete.cases(data$StartMonth, data$EndMonth), ]
  
  # Create date variables
  data$Date.start <- as.Date(paste0(data$StartYear, "-", data$StartMonth, "-01"))
  data$Date.end <- as.Date(paste0(data$EndYear, "-", data$EndMonth, "-01"))
  
  # Rename countries
  replacements <- c(
    "Czechoslovakia"                              = "Czech Republic (the)",
    "Germany Fed Rep"                             = "Germany",
    "Korea (the Republic of)"                     = "Korea South",
    "Korea (the Democratic People's Republic of)" = "Korea North",
    "Serbia Montenegro"                           = "Serbia",
    "Yugoslavia"                                  = "Serbia"
  )
  data$country_Emdat <- ifelse(data$country_Emdat %in% names(replacements), replacements[data$country_Emdat], data$country_Emdat)
  
  # Create ISO codes
  data$iso3c <- countrycode(data$country_Emdat, "country.name", "iso3c")
  
  # Drop NA ISO codes
  data <- data[complete.cases(data$iso3c), ]
  
  # Subset variables
  data <- data[c("DisNo", "iso3c", "DisasterSubgroup", "Date.start", "Date.end")]
  
  # Sort dataset
  data <- data[order(data$iso3c, data$Date.start), ]
  
  return(data)
}

# Apply function for different thresholds
EM_dat_1k <- process_EmDat_1(EMDAT, 1000)
EM_dat_5k <- process_EmDat_1(EMDAT, 5000)
EM_dat_50k <- process_EmDat_1(EMDAT, 50000)
EM_dat_100k <- process_EmDat_1(EMDAT, 100000)
  
  
  
```

#### Getting it in a country-year-month panel format
```{r}

process_EmDat_2 <- function(df, df_basey) {
# Reshape dataset
df <- df %>%
  group_by(iso3c, DisNo, DisasterSubgroup) %>%
  summarise(date = list(seq(floor_date(min(Date.start), unit = "month"),
                            floor_date(max(Date.end), unit = "month"),
                            by = "month"))) %>%
  unnest(cols = c(date))

# Sort dataframe
df <- df[order(df$iso3c, df$date), ]

# Create dummy for count
df$count <- 1

# Count events
df <- df %>%
  group_by(iso3c, DisasterSubgroup, date) %>%
  summarise(count = sum(count))

# Reshape
df <- dcast(df, date + iso3c ~ DisasterSubgroup)

# Merge with vector dates countries
df$Date_month <- as.yearmon(df$date)
df <- left_join(df_basey, df, by = c("date_month" = "Date_month", "iso3c" = "iso3c"))

# List variables
List <- setdiff(names(df), c("country", "year", "iso3c", "count", "date_month", "date"))

# Assign 0s
df <- df %>%
  mutate(across(all_of(List), ~ replace_na(., 0)))

# Drop date
df <- dplyr::select(df, -date)

# Create variable year
df$year <- as.double(substr(df$date_month, 5, 9))


# Create dummy variables
df[List] <- lapply(df[List], function(x) as.integer(x > 0))
colnames(df)[colnames(df) %in% List] <- paste0(colnames(df)[colnames(df) %in% List], "_dummy")

# List variables
List <- grep("_dummy$", names(df), value = TRUE)

# Create lags
df <- Lag_12(df, iso3c, List)

# Clean names
df <- janitor::clean_names(df)

  
  return(df)
}

# Process each dataset
EM_dat_1k_processed_2 <- process_EmDat_2(EM_dat_1k, df_Base_YM)
EM_dat_5k_processed_2 <- process_EmDat_2(EM_dat_5k, df_Base_YM)
EM_dat_50k_processed_2 <- process_EmDat_2(EM_dat_50k, df_Base_YM)
EM_dat_100k_processed_2 <- process_EmDat_2(EM_dat_100k, df_Base_YM)

```

#### Getting it in a country-year panel format
```{r}
process_EmDat_3 <- function(df, df_basey) {
  df <- df %>%
    group_by(iso3c, year) %>%
     dplyr::summarize(
      across(ends_with("_dummy"), sum)
    )
  
  # create dummy variables
  List <- setdiff(names(df), c("iso3c", "year"))
  for (variable in List) {
    new_name <- sub("_n_m$", "_dummy", variable)
    df[[new_name]] <- ifelse(df[[variable]] == 0, 0, 1)
  }
  
  # Merge with Base
  df <- left_join(df_basey, df, by = c("year", "iso3c"))
  
  # Assign 0s
  df <- df %>%
    mutate(across(List, ~ replace_na(., 0)))
  
  # Lag 12
  df <- Lag_12(df, iso3c, List)
  
  # Clean names
  df <-  janitor::clean_names(df)
  
  return(df)
}

# Process each dataset
EM_dat_1k_processed_3 <- process_EmDat_3(EM_dat_1k_processed_2, df_Base_Y)
EM_dat_5k_processed_3 <- process_EmDat_3(EM_dat_5k_processed_2, df_Base_Y)
EM_dat_50k_processed_3 <- process_EmDat_3(EM_dat_50k_processed_2, df_Base_Y)
EM_dat_100k_processed_3 <- process_EmDat_3(EM_dat_100k_processed_2, df_Base_Y)

```

#### Add suffix to vars of different datasets
```{r}

# List of variable names to change
List<- sort(unique(ls(EM_dat_1k_processed_3[ , names(EM_dat_1k_processed_3) %!in% c("iso3c",
                                                                                    "year",
                                                                                    "country")])))  

# Call the function to add "_1k" to the specified variables
EM_dat_1k_processed_3 <- rename_columns(EM_dat_1k_processed_3, "_1k", List)
# Call the function to add "_5k" to the specified variables
EM_dat_5k_processed_3 <- rename_columns(EM_dat_5k_processed_3, "_5k", List)
# Call the function to add "_50k" to the specified variables
EM_dat_50k_processed_3 <- rename_columns(EM_dat_50k_processed_3, "_50k", List)
# Call the function to add "_100k" to the specified variables
EM_dat_100k_processed_3 <- rename_columns(EM_dat_100k_processed_3, "_100k", List)

```


#### Calculate number of fat per year 
```{r}

# Function to process dataset
process_EmDat_fat <- function(data) {

    # Subset years
  data <- subset(data, StartYear >= 1980)
  
  # Drop technological disasters
  data <- subset(data, DisasterGroup == "Natural")
  
  # Select variables of interest
  data <- data[c("DisNo", "StartYear", "EndYear", "Country", "DisasterSubgroup", "TotalDeaths")]
  

  # Rename countries
  replacements <- c(
    "Czechoslovakia"                              = "Czech Republic (the)",
    "Germany Fed Rep"                             = "Germany",
    "Korea (the Republic of)"                     = "Korea South",
    "Korea (the Democratic People's Republic of)" = "Korea North",
    "Serbia Montenegro"                           = "Serbia",
    "Yugoslavia"                                  = "Serbia"
  )

  data$Country <- ifelse(data$Country %in% names(replacements), replacements[data$Country], data$Country)
  
  # Create ISO codes
  data$iso3c <- countrycode(data$Country, "country.name", "iso3c")
  
  # Drop NA ISO codes
  data <- data[complete.cases(data$iso3c), ]
  
  # Subset variables
  data <- data[c("iso3c", "DisasterSubgroup", "EndYear","TotalDeaths")]
  

     # List variables
  List <-  c("TotalDeaths")
  # Assign 0s
  data <- data %>%
    mutate(across(all_of(List), ~ replace_na(., 0)))

  # Count events
  data <- data %>%
  group_by(iso3c, EndYear) %>%
  summarise(TotalDeaths = sum(TotalDeaths))

    names(data)[names(data) == "EndYear"] <- "year"
    names(data)[names(data) == "TotalDeaths"] <- "dis_death"


    
     # merge with base  
  data <- left_join(df_Base_Y, data, by = c("year" = "year", "iso3c" = "iso3c"))
  
     # List variables
  List <-  c("dis_death")
  # Assign 0s
  data <- data %>%
    mutate(across(all_of(List), ~ replace_na(., 0)))

      
 #list variables aiddata 
List<- c("dis_death")

## lag variables of 1 to 2 years
data<-Lag_12(data, iso3c, List) 
  
  
  return(data)
}

# Apply function for different thresholds
EM_dat_fat <- process_EmDat_fat(EMDAT)


```


## Merge different Mdat datasets
```{r}
df_EMDAT_full <- left_join(EM_dat_1k_processed_3, EM_dat_5k_processed_3, by = c("year" = "year", "iso3c" = "iso3c","country" = "country"))
df_EMDAT_full <- left_join(df_EMDAT_full, EM_dat_50k_processed_3, by = c("year" = "year", "iso3c" = "iso3c","country" = "country"))
df_EMDAT_full <- left_join(df_EMDAT_full, EM_dat_100k_processed_3, by = c("year" = "year", "iso3c" = "iso3c","country" = "country"))

# Drop country
df_EMDAT_full <- dplyr::select(df_EMDAT_full, -country)
```


# Merge datasets main independent and controls
```{r}
## add world bank variables
#df_Ind_var <- left_join(df_UNcomtrade_main, df_WorldBank, by = c("year" = "year", "iso3c" = "iso3c"))
## add humanitarian dfs
df_Ind_var <- left_join(df_Vdem_s, df_HOD_cy, by = c("year" = "year", "iso3c" = "iso3c"))
## add vdem indexes
df_Ind_var <- left_join(df_Ind_var, df_WorldBank, by = c("year" = "year", "iso3c" = "iso3c"))
## add conf events
df_Ind_var <- left_join(df_Ind_var, df_UCDP_GED_Y, by = c("year" = "year", "iso3c" = "iso3c"))
## add membership
df_Ind_var <- left_join(df_Ind_var, df_IGOs, by = c("year" = "year", "iso3c" = "iso3c"))
## add donors
df_Ind_var <- left_join(df_Ind_var, df_donors, by = c("year" = "year", "iso3c" = "iso3c"))
## add geo and colonial eritage
df_Ind_var <- left_join(df_Ind_var, df_rugged, by = c("iso3c" = "iso3c"))
## add Mdata
df_Ind_var <- left_join(df_Ind_var, df_EMDAT_full, by = c("year" = "year", "iso3c" = "iso3c"))
## add fat Mdata
df_Ind_var <- left_join(df_Ind_var, EM_dat_fat, by = c("year" = "year", "iso3c" = "iso3c"))
## add KOF index
df_Ind_var <- left_join(df_Ind_var, df_KOFIndex, by = c("year" = "year", "iso3c" = "iso3c"))
## Add RPE
df_Ind_var <- left_join(df_Ind_var, df_rpc, by = c("year" = "year", "iso3c" = "ISO3"))

```


# Robustness test fill missing values
```{r}
# #list variables aiddata sectoral
# List<- colnames(df_Ind_var)[!colnames(df_Ind_var) %in% c("iso3c",
#                                                              "year",
#                                                              "country")]
# 
# ## lag variables of 1 to 2 years
# df_Ind_var<-df_Ind_var %>% group_by(iso3c) %>% fill(List, .direction="down")
```


## Export dataset to Nextcoloud
```{r}
# Set path for Marco nextcloud
path<-"C:/Users/marco/Nextcloud/Global Solidarity/Compiled"


## create path
folder_path <- file.path(path,"df_Ind_var_v2.rds")
## save file
saveRDS(df_Ind_var, folder_path)

```

# Export
## Set subfolder name
```{r}
sub_folder_name<-"Compiled"
```

## Create folder
```{r}

# Combine the desktop path with the folder name
folder_path <- file.path(desktop_path, main_folder_name, sub_folder_name)

# Check if the folder exists
if (!file.exists(folder_path)) {
  # If the folder doesn't exist, create it
  dir.create(folder_path)
  cat("Folder", main_folder_name, "created on the desktop.\n")
} else {
  # If the folder already exists, do nothing
  cat("Folder", main_folder_name, "already exists on the desktop.\n")
}
```

## Export file
```{r}
#saving it
namefile<-"df_Ind_var.rds"
folder_path_wb <- file.path(desktop_path, main_folder_name, sub_folder_name, namefile)
#folder_path_wb <-(paste0(userpath,"Nextcloud/Global Solidarity/Compiled/df_Ind_var.rds"))
saveRDS(df_Ind_var, folder_path_wb)

```


```{r}

```



